---
title: "COVID-19 in NRW"
author: "Thi Phuong Huynh"
date: "2/7/2022"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true # able of contents to the left, visible even when the document is scrolled
---

# Set up

Date: <b>`r format(Sys.Date(), "%B %d, %Y")`</b>

All computations were performed with `r R.Version()$version.string`.


```{r setup, include=FALSE}

rm(list = ls())
knitr::opts_chunk$set(fig.retina = 1, fig.height = 7, fig.width = 14,
                      echo = FALSE, message = FALSE, warning = FALSE,
                      results='hide')
Sys.setlocale("LC_TIME", "C")
BEGIN_RMD <- Sys.time() # Keeping track of running time
options(warn = 1) # If warn is one, warnings are printed as they occur.



#Loading package
library(reshape2, ggplot2)
library('ggplot2')
library('scales')
library(tidyverse)
library(surveillance)
library(lubridate)
library(broom)
library(runjags)
# library(rjags) check !
library(EpiEstim)
library(incidence)
library(epitools)
library(zoo) # rolling average
library(readxl)

path_data <- paste0("C:/Users/huynh/sciebo/NRW_descriptive/data/")
path_result <- paste0("C:/Users/huynh/sciebo/NRW_descriptive/results/COVID_19/")

```

#changeable variable

```{r}

#pop
NRW_pop <- 17925570
NRW_under12 <- 2014762
NRW_vacc <- NRW_pop - NRW_under12
start_day <- as.Date("2020-02-27")# data before this day won't be counted
current_date <-as.Date("2021-12-29") # data is available up to this date

colfunc <- colorRampPalette(c("black", "white"))
colfunc(19)
palette <- c("red","#003366", "olivedrab3","#336699", "#CCFFFF", "#028482", "#663399", "#990033", "#FF3333", "royalblue1","#FF9900", 
             "#266A2E", "#55D43F", "#404040", "#C87533", "#DCDCDC", "#FFDE00", "#F1B2E1", "#FF717E", "maroon3")
# print(palette)
# scales::show_col(palette)

# sequencial palette
palette1 <- c("#8e0152","#c51b7d", "#de77ae","#f1b6da", "#fde0ef",
              "#276419", "#4d9221", "#7fbc41","#b8e186","#e6f5d0",
              "#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
              "#e0e0e0", "#bababa", "#878787", "#4d4d4d", "#1a1a1a")



# print(palette1)
# scales::show_col(palette1)


```

# Data

```{r read in}
#(1) Linelist_COVID-19 in NRW
dat = read.csv(paste0(path_data,"211229_Fall-Liste.csv"), sep=";", encoding="UTF-8")# encoding="UTF-8" : umlaut character


#(2) age distribution in NRW
## age: 90 mean 90 and older
age_nrw = read.csv(paste0(path_data,"NRW_population_by age.csv"))


#(3) hospitalization
hosp <- read_excel(paste0(path_data,"211229 NRW dateninput modellierungen wwu.xlsx"), sheet = 2)

```

## cleaning data

```{r}

#(1) Linelist_covid-19 in NRW
colnames(dat)
dat <- dat %>% select(-contains("InterneRef")) # remove a col
names(dat) <- c("rep_date","county", "disease_start", "age",'hosp') #rename

dat$rep_date<- as.Date(dat$rep_date, "%Y-%m-%d")
dat$disease_start<- as.Date(dat$disease_start, "%Y-%m-%d")
dat$county <- as.factor(dat$county)
dat$rep_week <- as.integer((as.Date(dat$rep_date)-as.Date("2020-01-01"))/7+1)
dat$maxrepweek <- max(dat$rep_week) 

#revert week (number) to start date of a week: 1/1/2020 is on Wednesday 
## So Wednesday is start of a week
dat$rep_week_date <- lubridate::ymd( "2020-01-01" ) + lubridate::weeks(dat$rep_week-1)# indicated date starts week 2 of the year
dat$rep_week_date <- as.Date(dat$rep_week_date)


# age group
dat$agegroup<- dat$age
dat$agegroup <- cut(dat$agegroup, breaks=c(-Inf, 4, 9,14, 19,24,29,34,39,44,49,54,59,64,69,74,79,84,89, Inf))
dat$agegroup <- factor(dat$agegroup, levels=c("(-Inf,4]", "(4,9]", "(9,14]", "(14,19]", "(19,24]", "(24,29]", "(29,34]", "(34,39]", "(39,44]", "(44,49]", "(49,54]", "(54,59]", "(59,64]", "(64,69]", "(69,74]", "(74,79]", "(79,84]", "(84,89]",  "(89, Inf]"),
                       labels=c("0-4","5-9","10-14", "15-19", "20-24", "25-29", "30-34", "35-39",
                                "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74",
                                "75-79", "80-84", "85-89", ">90"), ordered=T)

# # Some logical cleaning:
# #set the rep_date for all obs to missing with reporting dates before 20th of Feb
# dat$rep_date[dat$rep_date<"2020-02-20"]<-NA
# 
# #set all disease start dates to missing if disease start before 1st of Feb or after date of current_date
# dat$disease_start[dat$disease_start<"2020-02-01"]<-NA
# dat$disease_start[dat$disease_start>dat$maxrepdate]<-NA
# 
# #set all disease start dates to missing for which the disease start date was more than 7 days after the rep date
# dat$disease_start[as.numeric(dat$rep_date - dat$disease_start) < -7] <- NA
# dat$disease_start[as.numeric(dat$rep_date - dat$disease_start) > 30] <- NA
# 
# #set implausible age to NA
# dat$age2<-dat$age
# dat$age2[dat$age<0 | dat$age>110] <- NA


#(2) age distribution in NRW

age_nrw$agegroup<- age_nrw$age
age_nrw$agegroup <- cut(age_nrw$agegroup, breaks=c(-Inf, 4, 9,14, 19,24,29,34,39,44,49,54,59,64,69,74,79,84,89, Inf))
age_nrw$agegroup <- factor(age_nrw$agegroup, levels=c("(-Inf,4]", "(4,9]", "(9,14]", "(14,19]", "(19,24]", "(24,29]", "(29,34]", "(34,39]", "(39,44]", "(44,49]", "(49,54]", "(54,59]", "(59,64]", "(64,69]", "(69,74]", "(74,79]", "(79,84]", "(84,89]",  "(89, Inf]"),
                       labels=c("0-4","5-9","10-14", "15-19", "20-24", "25-29", "30-34", "35-39",
                                "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74",
                                "75-79", "80-84", "85-89", ">90"), ordered=T)


age_nrw <- age_nrw %>%group_by(agegroup)%>%
  dplyr::summarise(pop_n =sum(pop_n))
# sum pop of all age
age_nrw_all <- age_nrw %>%dplyr::summarise(pop_n =sum(pop_n))%>%
  ungroup()%>%
  mutate(agegroup = "allAge")
age_nrw_all <- age_nrw_all[,c(2,1)] #arrange col order for merging data later
age_nrw_all <- rbind(age_nrw, age_nrw_all) # add all age pop row
                 
dat<- merge(dat, age_nrw, by="agegroup", all=T)# add nrw pop distribution by age


# remove rep week 8 because of insufficient data 
dat <- dat %>% filter(rep_week >=10)#

#(3) hospitalization
colnames(hosp)
colnames(hosp) <- c("rep_date","total","normal","intensive","ventilation")

hosp$rep_date<- as.Date(hosp$rep_date)
hosp$rep_week <- as.integer((as.Date(hosp$rep_date)-as.Date("2020-01-01"))/7+1)
hosp$maxrepweek <- max(hosp$rep_week) 

#revert week (number) to start hospe of a week: 1/1/2020 is on Wednesday 
## So Wednesday is start of a week
hosp$rep_week_date <- lubridate::ymd( "2020-01-01" ) + lubridate::weeks(hosp$rep_week-1)# indicated date starts week 2 of the year
hosp$rep_week_date <- as.Date(hosp$rep_week_date)


```

##add allage (new row)

A long week each agegroup, Allage (new row)is also added. 

###date level

```{r}
##sum cases of each agegroup by date
dat_date <- dat %>%
  group_by(rep_date,rep_week_date,rep_week,agegroup) %>%
  dplyr::summarise(case=n()) %>% #sum cases per date by age groups
  ungroup() 

## sum cases of all age by week
dat_allAge <- dat %>%
  group_by(rep_date,rep_week_date,rep_week) %>%
  dplyr::summarise(case=n()) %>% # sum cases per date in all age groups
  ungroup()%>%
  mutate(agegroup = "allAge")
dat_allAge <- dat_allAge[,c(1:3,5,4)] #arrange col order as in 'dat_date' for merging data later

dat_date <- rbind(dat_date, dat_allAge)# add cases of allAge


dat_date <- merge(dat_date,age_nrw_all, by ="agegroup") # add pop to dat_date for weghing

# rolling average

dat_date <- dat_date %>%mutate(
      case_7da = zoo::rollmean(case, k = 7, fill = NA))


dat_date$case_per100k<- dat_date$case/dat_date$pop_n*100000


#division 0
dat_date$case_per100k_grouped <- cut(dat_date$case_per100k, breaks=c(-Inf, 5, 10, 15, 20, 35,50,100,150,200,300,Inf))
dat_date$case_per100k_grouped <- factor(dat_date$case_per100k_grouped, levels=c("(-Inf,5]", "(5,10]", "(10,15]", "(15,20]", "(20,35]", "(35,50]","(50,100]", "(100,150]", "(150,200]", "(200,300]", "(300, Inf]"),
                      labels=c("0-5",">5-10",">10-15", ">15-20", ">20-35", ">35-50", ">50-100", ">100-150",">150-200", ">200-300", ">300"), ordered=T)




```

###week level

####case

```{r}
##sum cases of each agegroup by week
dat_week <- dat %>%
  group_by(rep_week_date,rep_week,agegroup) %>%
  dplyr::summarise(case=n()) %>% #sum cases per week by age groups
  ungroup() 

## sum cases of all age by week
dat_allAge <- dat %>%
  group_by(rep_week_date,rep_week) %>%
  dplyr::summarise(case=n()) %>% # sum cases per week in all age groups
  ungroup()%>%
  mutate(agegroup = "allAge")

dat_allAge <- dat_allAge[,c(1,2,4,3)] #arrange col order as in 'dat_week' for merging data later

dat_week <- rbind(dat_week, dat_allAge)# add cases of allAge

dat_week <- merge(dat_week,age_nrw_all, by ="agegroup") # add pop to dat_week for weghing

# 
# dat_week <- dat_week %>% group_by(rep_week) %>% mutate(percent_repweek=case/sum(case))
# 
# 
# # Summary data at week level
# dat_date <- dat %>% group_by(rep_date, agegroup) %>% dplyr::summarise(case=n())
# dat_date <- dat_date %>% filter(rep_date > start_day)
# dat_date <- dat_date %>% group_by(rep_date) %>% mutate(percent_repdate=case/sum(case))


dat_week$case_per100k<- dat_week$case/dat_week$pop_n*100000


#division 0
dat_week$case_per100k_grouped <- cut(dat_week$case_per100k, breaks=c(-Inf, 5, 10, 15, 20, 35,50,100,150,200,300,Inf))
dat_week$case_per100k_grouped <- factor(dat_week$case_per100k_grouped, levels=c("(-Inf,5]", "(5,10]", "(10,15]", "(15,20]", "(20,35]", "(35,50]", "(50,100]", "(100,150]", "(150,200]", "(200,300]", "(300, Inf]"),
                            labels=c("0-5",">5-10",">10-15", ">15-20", ">20-35", ">35-50", ">50-100", ">100-150", ">150-200", ">200-300", ">300"), ordered=T)




```

####hosp

```{r}
##sum cases of each agegroup by week
hosp_week <- dat %>%filter(hosp=="Ja")%>%
  group_by(rep_week_date,rep_week,agegroup) %>%
  dplyr::summarise(case=n()) %>% #sum cases per week by age groups
  ungroup() 
## sum hosp cases of all age by week
hosp_allAge <- dat %>%filter(hosp=="Ja")%>%
  group_by(rep_week_date,rep_week) %>%
  dplyr::summarise(case=n()) %>% # sum cases per week in all age groups
  ungroup()%>%
  mutate(agegroup = "allAge")

hosp_allAge <- hosp_allAge[,c(1,2,4,3)] #arrange col order as in 'dat_week' for merging data later

hosp_week <- rbind(hosp_week, hosp_allAge)# add cases of allAge

hosp_week <- merge(hosp_week,age_nrw_all, by ="agegroup") # add pop to hosp_week for weghing


hosp_week$case_per100k<- hosp_week$case/hosp_week$pop_n*100000


#division 0
hosp_week$case_per100k_grouped <- cut(hosp_week$case_per100k, breaks=c(-Inf, 5, 10, 15, 20, 35,50,100,150,200,300,Inf))
hosp_week$case_per100k_grouped <- factor(hosp_week$case_per100k_grouped, levels=c("(-Inf,5]", "(5,10]", "(10,15]", "(15,20]", "(20,35]", "(35,50]", "(50,100]", "(100,150]", "(150,200]", "(200,300]", "(300, Inf]"),
                            labels=c("0-5",">5-10",">10-15", ">15-20", ">20-35", ">35-50", ">50-100", ">100-150", ">150-200", ">200-300", ">300"), ordered=T)

```

##sum case at county level

Variant of concern (earliest sample [place]- designated VOC)

- Alpha (20.09.2020 [UK]-18.12.2020)  -> wave 1,....

- Beta (05.2020[South Africa] - 14.01.2021) -> wave 2,....

- Gamma (11.2020 [Brasil]- 15.01.2021) -> wave 2, ...

- Delta (10.2020 [India]- 6.5.2021) -> wave2, wave 3,...

- Omicron (9.11.2021 [ South Africa] - 26.11.2021) -> wave 3, wave 4...

* Source: https://en.wikipedia.org/wiki/Variants_of_SARS-CoV-2

```{r}

#group data by county########
dat_county <- dat %>% group_by(county) %>%
  dplyr::summarise(case=n())%>%
  ungroup() 

dat_county_wave1 <- dat %>%filter(rep_date <= as.Date("2020-06-30")) %>% group_by(county) %>%
  dplyr::summarise(case_wave1=n())%>%
  ungroup() 
dat_county_wave2 <- dat %>%filter(rep_date > as.Date("2020-06-30")&rep_date <= as.Date("2021-02-04")) %>% group_by(county) %>%
  dplyr::summarise(case_wave2=n())%>%
  ungroup() 
dat_county_wave3 <- dat %>%filter(rep_date > as.Date("2021-02-04")&rep_date <= as.Date("2021-06-10")) %>% group_by(county) %>%
  dplyr::summarise(case_wave3=n())%>%
  ungroup() 
dat_county_wave4 <- dat %>%filter(rep_date > as.Date("2021-06-10")&rep_date <= as.Date("2021-12-30")) %>% group_by(county) %>%
  dplyr::summarise(case_wave4=n())%>%
  ungroup() 

# dat_county1 <- left_join (dat_county,dat_county_wave1,dat_county_wave2,dat_county_wave3,dat_county_wave4, by="county")
dat_county <- left_join (dat_county,dat_county_wave1)
dat_county <- left_join (dat_county,dat_county_wave2)
dat_county <- left_join (dat_county,dat_county_wave3)
dat_county <- left_join (dat_county,dat_county_wave4)
rm(dat_county_wave1,dat_county_wave2,dat_county_wave3,dat_county_wave4)

# write.csv(dat_county,paste0(path_data,"case_county_waves.csv"))


```

# NRW pop distribution

```{r}
# pop distribution  
  
age_nrw %>%
  ggplot(aes(x = agegroup, y= pop_n/1000)) +  # unit: thousand
  geom_bar(stat="identity", fill = " dark blue")+
  # facet_grid(row = vars(agegroup))+
  # scale_y_continuous(labels = scales::percent_format()) +
  # scale_fill_manual(values=palette1, name="Age group") +
  labs(y = "Number of inhabitants [thousand]") +
  ggtitle("NRW_ pop distribution")+
  theme(axis.text.x = element_text(colour = "black", size = 10, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 15, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = 14, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = 12, face = "bold"))

# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```


# COVID-19 over time 

## Heatmap: by age

### Case

```{r}
dat_week %>% 
  filter(!is.na(agegroup)) %>%
  ggplot(aes(rep_week_date, agegroup)) +
  geom_tile(aes(fill=case_per100k_grouped), colour = "black")+
  geom_text(aes(label = round(case_per100k)), size = 2, colour = "#585858") + #size of number in each cell
  #division 0
  scale_fill_manual(values=c("#FFF7FC","#EDE7F3", "#D0D1E6", "#A6BDDC", "#74AAD0",
                             "#3691C0", "#0470B0", "#044E7B", "#333F50", "#404040", "#262626")) +
  ## division 1,2,3
  # scale_fill_brewer(palette = "Blues")+ #BuPu, BuGn, Blues, Oranges,Reds,....
  labs(fill = "incidence \n(per 100k)", x="")+
  ggtitle("NRW_ weekly COVID-19 Incidence per 100k 
")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.position="right",
        legend.title=element_text(size=18, colour = "black", face = "bold") ,
        legend.text=element_text(size=17, colour = "black"),
        axis.title = element_text(size=18, face="bold", colour = "black"),
        plot.title = element_text(face="bold", size=15, hjust=0.5),
        axis.text.x = element_text(size = 10,  hjust = 1, colour = "black", angle = 30, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold")) + 
  scale_x_date(date_labels="%Y-%m-%m", date_breaks = "30 days", expand = c(0, 0)) +
  # scale_x_continuous(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0))

# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)

```


### Hosp

```{r}
hosp_week %>%
  ggplot(aes(rep_week_date, agegroup)) +
  geom_tile(aes(fill=case_per100k_grouped), colour = "black")+
  geom_text(aes(label = round(case_per100k)), size = 2, colour = "#585858") + #size of number in each cell
  #division 0
  scale_fill_manual(values=c("#FFF7FC","#EDE7F3", "#D0D1E6", "#A6BDDC", "#74AAD0",
                             "#3691C0", "#0470B0", "#044E7B", "#333F50", "#404040", "#262626")) +
  ## division 1,2,3
  # scale_fill_brewer(palette = "Blues")+ #BuPu, BuGn, Blues, Oranges,Reds,....
  labs(fill = "incidence \n(per 100k)", x="")+
  ggtitle("NRW_ weekly COVID-19 hospitalised incidence per 100k 
")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.position="right",
        legend.title=element_text(size=18, colour = "black", face = "bold") ,
        legend.text=element_text(size=17, colour = "black"),
        axis.title = element_text(size=18, face="bold", colour = "black"),
        plot.title = element_text(face="bold", size=15, hjust=0.5),
        axis.text.x = element_text(size = 10,  hjust = 1, colour = "black", angle = 30, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold")) + 
 scale_x_date(date_labels="%Y-%m-%m", date_breaks = "30 days", expand = c(0, 0)) +
  # scale_x_continuous(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0))

# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)

```


## Histogram: by age
### No pop. weighing
#### Case

```{r}


#create data structure for histogram
#case prop_all age group################################
histo_setup <- dat%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n()) 
# histo_setup$maxrepweek <- max(histo_setup$rep_week)


dat%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n())%>%
  ggplot(aes(x=rep_week_date, y=case_n, fill=agegroup)) + 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_fill_manual(values=palette, name="Age group") +
   labs(y="Propotion of reported case",x=" ")+
  ggtitle(" Covid-19 reported  weekly in NRW")+
 scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", expand = c(0, 0)) +
theme(axis.text.x = element_text(colour = "black", size = 10,
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 15, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = 14, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = 12, face = "bold"))



# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```

#### Hosp

```{r}

dat%>%filter(hosp=="Ja")%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n())%>%
  ggplot(aes(x=rep_week_date, y=case_n, fill=agegroup)) + 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_fill_manual(values=palette, name="Age group") +
   labs(y="Propotion of reported case",x=" ")+
  ggtitle(" Covid-19 hospitalisation weekly in NRW")+
 scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", expand = c(0, 0)) +
theme(axis.text.x = element_text(colour = "black", size = 10, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 15, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = 14, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = 12, face = "bold"))


# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```

### Pop. weighing
#### Case

```{r}


#create data structure for histogram
#case prop_all age group################################
histo_setup <- dat%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n()) 
# histo_setup$maxrepweek <- max(histo_setup$rep_week)


dat%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n())%>%
  ggplot(aes(x=rep_week_date, y=case_n/pop_n*100000, fill=agegroup)) + # scale by age's pop 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_fill_manual(values=palette, name="Age group") +
   labs(y="Propotion of reported case per 100k",x=" ")+
  ggtitle(" Covid-19 reported  weekly in NRW")+
 scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", expand = c(0, 0)) +
theme(axis.text.x = element_text(colour = "black", size = 10, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 15, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = 14, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = 12, face = "bold"))


# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```

#### Hosp

```{r}

dat%>%filter(hosp=="Ja")%>%
  group_by(rep_week,rep_week_date, agegroup,pop_n) %>% dplyr::summarise(case_n=n())%>%
  ggplot(aes(x=rep_week_date, y=case_n/pop_n*100000, fill=agegroup)) + # scale by age's pop 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_fill_manual(values=palette, name="Age group") +
   labs(y="Propotion of reported case per 100k",x=" ")+
  ggtitle(" Covid-19 hospitalisation weekly in NRW")+
 scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", expand = c(0, 0)) +
theme(axis.text.x = element_text(colour = "black", size = 10, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 15, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = 14, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = 12, face = "bold"))


# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```




## Regardless of age
### daily
#### Case

```{r}

# weighing for pop
 dat%>%
  group_by(rep_date) %>% dplyr::summarise(case_n=n())%>% #count case by week
  ggplot()+
  geom_line(aes(y=case_n/NRW_pop*100000, x=rep_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported cases per 100k pop.") +
  ylim(0,60)+
  ggtitle("COVID-19 in NRW_ daily report")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))


# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)

```

#### Hosp

```{r}

# Weighing for pop
 dat%>%filter(hosp=="Ja")%>%
  group_by(rep_date) %>% dplyr::summarise(case_n=n())%>% #count case by week
  ggplot()+
  geom_line(aes(y=case_n/NRW_pop*100000, x=rep_date), size=1, colour="blue") +
   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported hospitalisation per 100k pop.") +
   ylim(0,6.0)+
  ggtitle("COVID-19 hospitalisation in NRW_ daily report")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))



# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)

```

#### ICU
* This data from **211229 NRW dateninput modellierungen wwu** 

The number is much higher than the line list. Check with Veronika again !

The earliest time is **06.04.2020**  while the line list's **19.02.2020**

Is normal mean non_hospitalization ? 

ICU = intensive + ventilation ??

```{r}
colnames(hosp)
hosp_melt <- melt(hosp, id.vars = c(1,6:8)) # id.vars indicate variables that you don't want to melt

# Weighing for pop
hosp_melt%>%
  ggplot()+
  geom_line(aes(y=value/NRW_pop*100000, x=rep_date,color=variable)) +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.", color="") +
  ylim(0,60)+
  ggtitle("COVID-19 in NRW_ daily report")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))


#Intensive case
hosp%>%
  ggplot()+
  geom_line(aes(y=intensive/NRW_pop*100000, x=rep_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
   ylim(0,6.0)+
  ggtitle("COVID-19 hospitalisation (intensive) in NRW_ daily")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))

#Ventilation case
hosp%>%
  ggplot()+
  geom_line(aes(y=ventilation/NRW_pop*100000, x=rep_date), size=1, colour="blue") +
   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
   ylim(0,6.0)+
  ggtitle("COVID-19 hospitalisation (ventilator) in NRW_ daily")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))


#ICU : intensive + ventilation ???
 hosp%>%
  group_by(rep_date) %>% dplyr::summarise(ICU= sum(intensive,ventilation))%>% #count case by week
  ggplot()+
  geom_line(aes(y=ICU/NRW_pop*100000, x=rep_date), size=1, colour="blue") +
   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
   ylim(0,7.0)+
  ggtitle("COVID-19 hospitalisation (ICU) in NRW_ daily")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))


  

# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)

```


### weekly
#### Case 

```{r}

# Weighing for pop 
dat%>%
  group_by(rep_week_date) %>% dplyr::summarise(case_n=n())%>% #count case by week
  ggplot()+
  geom_line(aes(y=case_n/NRW_pop*100000, x=rep_week_date), size=1, colour="blue") +
 scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported cases per 100k pop.") +
  ylim(0,400)+
  ggtitle("COVID-19 in NRW_ weekly report")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))



# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)



```

#### Hosp

```{r}

# Weighing for pop 
dat%>%filter(hosp=="Ja")%>%
  group_by(rep_week_date) %>% dplyr::summarise(case_n=n())%>% #count case by week
  ggplot()+
  geom_line(aes(y=case_n/NRW_pop*100000, x=rep_week_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported hospitalisation per 100k pop.") +
  ylim(0,40.0)+
  ggtitle("COVID-19 hospitalisation in NRW_ weekly report")+
  theme_classic()+
   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
         axis.title = element_text(colour = "black", size = 15, face = "bold"),
         legend.background = element_blank(),
         legend.key = element_blank(),
         legend.position = "right",
         legend.text = element_text(colour = "black", size = 15),
         legend.title = element_text(colour = "black", size = 16, face = "bold"),
         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
         strip.text = element_text(colour = "black", size = 10, face = "bold"))

# # No Weighing for pop 


# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)



```

#### ICU

```{r}

colnames(hosp) 
hosp_melt <- melt(hosp, id.vars = c(1,6:8)) # id.vars indicate variables that you don't want to melt

#Weighing for pop
hosp_melt%>%
  group_by(rep_week_date,variable) %>% dplyr::summarise(value=sum(value))%>% #count... by week
  ggplot()+
  geom_line(aes(y=value/NRW_pop*100000, x=rep_week_date,color=variable)) +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.", color="") +
  ylim(0,400)+
  ggtitle("COVID-19 in NRW_ weekly ")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))



# Intensive

hosp%>%
  group_by(rep_week_date) %>% dplyr::summarise(intensive=sum(intensive))%>% #count... by week
  ggplot()+
  geom_line(aes(y=intensive/NRW_pop*100000, x=rep_week_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
  ylim(0,40.0)+
  ggtitle("COVID-19 hospitalisation (intensive) in NRW_ daily")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

# Ventilation

hosp%>%
  group_by(rep_week_date) %>% dplyr::summarise(ventilation=sum(ventilation))%>% #count... by week
  ggplot()+
  geom_line(aes(y=ventilation/NRW_pop*100000, x=rep_week_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
  ylim(0,40.0)+
  ggtitle("COVID-19 hospitalisation (ventilation) in NRW_ daily")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

# ICU: intensive + Ventilation???

hosp%>%
  group_by(rep_week_date) %>% dplyr::summarise(ICU=sum(intensive ,ventilation))%>% #count... by week
  ggplot()+
  geom_line(aes(y=ICU/NRW_pop*100000, x=rep_week_date), size=1, colour="blue") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
               limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
               expand = c(0, 0)) +
  labs(x = " ", y = "Reported number per 100k pop.") +
  # ylim(0,40.0)+
  ggtitle("COVID-19 hospitalisation (ICU) in NRW_ daily")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)



```

