---
title: "Contact survey (COVIMOD) in NRW"
author: "Thi Phuong Huynh"
---

# set up

Date: <b>`r format(Sys.Date(), "%B %d, %Y")`</b>

All computations were performed with `r R.Version()$version.string`.

This work is adapted from Veronika's codes

```{r Options, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(fig.retina = 1, fig.height = 7, fig.width = 14,
                      echo = FALSE, message = FALSE, warning = FALSE,
                      results='hide')
Sys.setlocale("LC_TIME", "C")
BEGIN_RMD <- Sys.time() # Keeping track of running time
set.seed(75876342)
options(warn = 1) # If warn is one, warnings are printed as they occur.

path_data <- "C:/Users/huynh/sciebo/NRW_descriptive/COVIMOD/wave 1 to 32"
path_figures <- "C:/Users/huynh/sciebo/NRW_descriptive/results/covimod"
path_contact_pattern <- "C:/Users/huynh/sciebo/NRW_descriptive/results/covimod/contact_pattern"


# library loading
library(dplyr)
library(ggplot2)
library(tidyverse)
library(epiDisplay)
library(socialmixr)
library(data.table)
library(Hmisc)
library(epiDisplay)
library(summarytools)
library(patchwork)
library(gtsummary)
library(table1)
library(readxl)
library(reshape2)
library(kableExtra)
library(DescTools)
library(randomcoloR)
library(table1)
library(expss)
library(Cairo)
library(cowplot)
library(oxcgrt)
library(dplyr)
library(scales)
library(ggpubr)
library(stringr)
library(lubridate)
library(openxlsx)
library(tidyselect)


library(socialmixr)
# https://cran.r-project.org/web/packages/socialmixr/vignettes/introduction.html
library(RColorBrewer) # used to customize (heatmap) color
library(ggmosaic)
library(gridExtra)
library(grid)
library(Rmisc)
library(gtable)

```

#changeable variables

```{r}
#at which number should group contacts be truncated?
truncate <- 100 #question 100 ?
truncate_lshtm <- 50 #
current_wave <-32
base_size <- 10 # size of the font in plot


```

#Function

```{r Functions}
`%notin%` <- Negate(`%in%`)

my.render.cont <- function(x) {
  with(stats.apply.rounding(stats.default(x), digits=3, round.integers = F), 
       c("",
         "Mean (SD)"=sprintf("%s (%s)", MEAN, SD), 
         "Median (Min, Max)"=sprintf("%s [%s, %s]", MEDIAN, MIN, MAX),
         "Median (P25, P75)"=sprintf("%s [%s, %s]", MEDIAN, q25, q75)))
}

hh_contact_number <- function(x, new_id, wave) {
  dummy_hh <- data.table(x)
  dummy_hh <- dummy_hh %>% 
    filter(dummy_hh$hh_met_this_day == "Yes") # only hh member actually met!!!
  if(sum(is.na(dummy_hh$new_id)) > 0) { message("new_id has NAs!") }
  dummy_hh <- dummy_hh %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(hh_contact_n = n())
  return(dummy_hh)
}

non_hh_contact_number <- function(x, new_id, wave) {
  dummy_outside <- data.table(x)
  if(sum(is.na(dummy_outside$new_id)) > 0) { message("new_id has NAs!") }
  dummy_outside <- dummy_outside %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(non_hh_contact_n = n())
  
  dummy_work <- data.table(x)
  dummy_work <- dummy_work %>% 
    filter(place_work == "Yes")
  dummy_work <- dummy_work %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(work_contact_n = n())
  dummy_all <- merge(dummy_outside, dummy_work, by = c("new_id", "wave"), all = T)
  rm(dummy_outside, dummy_work)
  
  dummy_homeown <- data.table(x)
  dummy_homeown <- dummy_homeown %>% 
    filter(place_home_own == "Yes")
  dummy_homeown <- dummy_homeown %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(home_own_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_homeown, by = c("new_id", "wave"), all = T)
  rm(dummy_homeown)
  
  dummy_homeelse <- data.table(x)
  dummy_homeelse <- dummy_homeelse %>% 
    filter(place_home_else == "Yes")
  dummy_homeelse <- dummy_homeelse %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(home_else_contact_n = n())
  dummy_all <- merge(dummy_all, dummy_homeelse, by = c("new_id", "wave"), all = T)
  rm(dummy_homeelse)
  
  dummy_worship <- data.table(x)
  dummy_worship <- dummy_worship %>% 
    filter(place_worship=="Yes")
  dummy_worship <- dummy_worship %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(worship_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_worship, by = c("new_id", "wave"), all = T)
  rm(dummy_worship)
  
  dummy_transport <- data.table(x)
  dummy_transport <- dummy_transport %>% 
    filter(place_transport=="Yes")
  dummy_transport <- dummy_transport %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(transport_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_transport, by = c("new_id", "wave"), all = T)
  rm(dummy_transport)
  
  dummy_school <- data.table(x)
  dummy_school <- dummy_school %>% 
    filter(place_school=="Yes")
  dummy_school <- dummy_school %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(school_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_school, by = c("new_id", "wave"), all = T)
  rm(dummy_school)
  
  dummy_shop_essential <- data.table(x)
  dummy_shop_essential <- dummy_shop_essential %>% 
    filter(place_shop_essential=="Yes")
  dummy_shop_essential <- dummy_shop_essential %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(shop_essential_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_shop_essential, by = c("new_id", "wave"), all = T)
  rm(dummy_shop_essential)
  
  dummy_shop_non_essential <- data.table(x)
  dummy_shop_non_essential <- dummy_shop_non_essential %>% 
    filter(place_shop_non_essential=="Yes")
  dummy_shop_non_essential <- dummy_shop_non_essential %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(shop_non_essential_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_shop_non_essential, by = c("new_id", "wave"), all = T)
  rm(dummy_shop_non_essential)
  
  dummy_entertainment <- data.table(x)
  dummy_entertainment <- dummy_entertainment %>% 
    filter(place_entertainment=="Yes")
  dummy_entertainment <- dummy_entertainment %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(entertainment_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_entertainment, by = c("new_id", "wave"), all = T)
  rm(dummy_entertainment)
  
  dummy_sport <- data.table(x)
  dummy_sport <- dummy_sport %>% 
    filter(place_sport=="Yes")
  dummy_sport <- dummy_sport %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(sport_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_sport, by = c("new_id", "wave"), all = T)
  rm(dummy_sport)
  
  dummy_park <- data.table(x)
  dummy_park <- dummy_park %>% 
    filter(place_park=="Yes") 
  dummy_park <- dummy_park %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(park_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_park, by = c("new_id", "wave"), all = T)
  rm(dummy_park)
  
  dummy_healthcare <- data.table(x)
  dummy_healthcare <- dummy_healthcare %>% 
    filter(place_healthcare=="Yes") 
  dummy_healthcare <- dummy_healthcare %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(healthcare_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_healthcare, by = c("new_id", "wave"), all = T)
  rm(dummy_healthcare)
  
  dummy_beauty <- data.table(x)
  dummy_beauty <- dummy_beauty %>% 
    filter(place_beauty=="Yes") 
  dummy_beauty <- dummy_beauty %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(beauty_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_beauty, by = c("new_id", "wave"), all = T)
  rm(dummy_beauty)
  
  dummy_multiple <- data.table(x)
  dummy_multiple <- dummy_multiple %>% 
    filter(place_multiple==1) 
  dummy_multiple <- dummy_multiple %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(multiple_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_multiple, by = c("new_id", "wave"), all = T)
  rm(dummy_multiple)
  
  dummy_other <- data.table(x)
  dummy_other <- dummy_other %>%
    filter(!is.na(place_oth))
  dummy_other <- dummy_other %>%
    group_by(new_id, wave) %>%
    dplyr::summarise(oth_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_other, by = c("new_id", "wave"), all = T)
  rm(dummy_other)
  
  dummy_not_specified <- data.table(x)
  dummy_not_specified <- dummy_not_specified %>%
  filter(
    (place_home_own!="Yes" |is.na(place_home_own)) &
      (place_home_else!="Yes" |is.na(place_home_else)) &
      (place_work!="Yes" |is.na(place_work)) &
      (place_worship!="Yes" |is.na(place_worship)) &
      (place_transport!="Yes" |is.na(place_transport)) &
      (place_school!="Yes" |is.na(place_school)) &
      (place_shop_essential!="Yes" |is.na(place_shop_essential)) &
      (place_shop_non_essential!="Yes" |is.na(place_shop_non_essential)) &
      (place_entertainment!="Yes" |is.na(place_entertainment)) &
      (place_sport!="Yes" |is.na(place_sport)) &
      (place_park!="Yes" |is.na(place_park)) &
      (place_healthcare!="Yes" |is.na(place_healthcare)) &
      (place_beauty!="Yes" |is.na(place_beauty)) &
      (place_oth!=1 | is.na(place_oth))
        )
  dummy_not_specified <- dummy_not_specified %>% 
    group_by(new_id, wave) %>% 
    dplyr::summarise(not_specified_contact_n=n())
  dummy_all <- merge(dummy_all, dummy_not_specified, by = c("new_id", "wave"), all = T)
  rm(dummy_not_specified)
  
  
dummy_leisure <- data.table(dt_outside_all)
dummy_leisure <- dummy_leisure %>% 
  filter(place_home_own=="Yes" | place_home_else=="Yes" | place_worship=="Yes" | 
           place_shop_non_essential=="Yes" | place_entertainment=="Yes" | place_sport=="Yes" | place_park=="Yes" | place_beauty=="Yes") 
dummy_leisure <- dummy_leisure %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(leisure_contact_n=n())
dummy_all <- merge(dummy_all, dummy_leisure, by = c("new_id", "wave"), all = T)
rm(dummy_leisure)

dummy_other_combined<- data.table(dt_outside_all)
dummy_other_combined <- dummy_other_combined %>% 
  filter(place_transport=="Yes" | place_healthcare=="Yes" | place_oth==1 | place_shop_essential=="Yes") 
dummy_other_combined <- dummy_other_combined %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(other_combined_contact_n=n())
dummy_all <- merge(dummy_all, dummy_other_combined, by = c("new_id", "wave"), all = T)
rm(dummy_other_combined) 

  return(dummy_all)
}

my.bar.charts.incl.hh <- function(x) {
  dataset_long <- x
  p1 <- ggplot(dataset_long, 
               aes_string(x = "wave", y = "contact_n", fill = "contact_type")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format()) + 
    scale_fill_manual(values = palette,
                      name = "Setting") +
    xlab("Date") +
    ylab("Percent of overall contacts") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p1)
  
  text2eval <- paste0("table1::table1(~ ",
                      "contact_n",
                      " | contact_type,",
                      "data = dataset_long,",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
  
  p2 <- ggplot(dataset_long,
               aes_string(x = "wave", y = "contact_n", fill = "contact_type")) + 
    geom_bar(position = "fill", stat = "identity") +
    facet_wrap( ~ age_group) +
    scale_y_continuous(labels = scales::percent_format()) + 
    scale_fill_manual(values = palette,
                      name = "Setting") +
    xlab("Date") +
    ylab("Percent of overall contacts") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "none",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p2)
  
  text2eval <- paste0("table1::table1(~ ",
                      "contact_n",
                      " | contact_type + age_group,",
                      "data = dataset_long,",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
}

my.bar.charts.excl.hh <- function(x, exclude_hh_phrase) {
  dataset_long <- x
  p1 <- ggplot(subset(dataset_long, contact_type != exclude_hh_phrase), 
               aes_string(x = "wave", y = "contact_n", fill = "contact_type")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format()) + 
    scale_fill_manual(values = palette,
                      name = "Setting") +
    xlab("Date") +
    ylab("Percent of overall contacts") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p1)
  
  text2eval <- paste0("table1::table1(~ ",
                      "contact_n",
                      " | contact_type,",
                      "data = subset(dataset_long, contact_type != '", exclude_hh_phrase, "'),",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
  
  p2 <- ggplot(subset(dataset_long, contact_type != exclude_hh_phrase),
               aes_string(x = "wave", y = "contact_n", fill = "contact_type")) + 
    geom_bar(position = "fill", stat = "identity") +
    facet_wrap( ~ age_group) +
    scale_y_continuous(labels = scales::percent_format()) + 
    scale_fill_manual(values = palette,
                      name = "Setting") +
    xlab("Date") +
    ylab("Percent of overall contacts") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "none",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p2)
  
  text2eval <- paste0("table1::table1(~ ",
                      "contact_n",
                      " | contact_type + age_group,",
                      "data = subset(dataset_long, contact_type != '", exclude_hh_phrase, "'),",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
}

my.boxplots <- function(x, current_contact_variable, TITLE) {
  WORK <- grep("work", current_contact_variable)
  SCHOOL <- grep("school", current_contact_variable)
  
  if(length(WORK) > 0) {
    dataset_wide <- subset(x, job %in% has_work_contacts)
  } else if(length(SCHOOL) > 0) {
    dataset_wide <- subset(x, job == "Student/Pupil" | school %in% has_school_contacts)
  } else {
    dataset_wide <- x
  }
  
  dummy_N <- dataset_wide[, c("wave", current_contact_variable)]
  # # NOT RUN: Table 1 shows N per group
  # dummy_N <- dummy_N %>% 
  #   group_by(wave) %>% 
  #   dplyr::summarise(N_ID=n())
  # levels(dataset_wide[, "wave"]) <- paste0(dummy_N$wave, " (n =",
  #                                          dummy_N$N_ID, ")")
  # rm(dummy_N)
  
  p1 <- ggplot(dataset_wide, aes_string(x = "wave", y = current_contact_variable)) +  
    geom_boxplot() + 
    scale_y_continuous(trans=scales::pseudo_log_trans(base = 10))+ 
    xlab("Date") +
    ylab("Number of contacts") +
    ggtitle(TITLE) +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p1)
  
  text2eval <- paste0("table1::table1(~ ",
                      current_contact_variable,
                      " | wave, data = dataset_wide,",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
  
  names(dummy_N) <- c("wave", "contact_n")
  dummy_N <- dummy_N %>%
    group_by(wave) %>%
    summarise(MEAN = mean(contact_n),
              SD = sd(contact_n),
              MEDIAN = median(contact_n),
              MIN = min(contact_n),
              MAX = max(contact_n),
              IQR = IQR(contact_n))

  p2 <- ggplot(data = dummy_N) +  
    geom_point(aes_string(x = "wave", y = "MEAN"), colour = "red", size = 1.25, shape = 15) +
    geom_line(aes_string(x = "wave", y = "MEAN"), colour = "red", group = "wave") +
    geom_point(aes_string(x = "wave", y = "MEDIAN"), colour = "blue", size = 1.25, shape = 17) +
    geom_line(aes_string(x = "wave", y = "MEDIAN"), colour = "blue", group = "wave") +
    scale_y_continuous(limits = c(0, max(c(1, dummy_N$MEAN, dummy_N$MEDIAN)))) + 
    xlab("Date") +
    ylab("Mean contacts (red squares) /\nMedian number of contacts (blue circles)") +
    ggtitle(TITLE) +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p2)
  
  p3 <- ggplot(dataset_wide, aes_string(x = "wave", y = current_contact_variable)) +  
    geom_boxplot() + 
    facet_wrap( ~ age_group) +
    # stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +
    scale_y_continuous(trans=scales::pseudo_log_trans(base = 10))+ 
    xlab("Date") +
    ylab("Number of contacts") +
    ggtitle(TITLE) +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = base_size, 
                                     angle = 45, hjust = 1, vjust = 1),
          axis.text.y = element_text(colour = "black", size = base_size),
          axis.title = element_text(colour = "black", size = base_size),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(colour = "black", size = base_size),
          legend.title = element_text(colour = "black", size = base_size, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold")
    )
  print(p3)
  
  text2eval <- paste0("table1::table1(~ ",
                      current_contact_variable,
                      " | wave + age_group, data = dataset_wide,",
                      "render.categorical='FREQ (PCTnoNA%)',",
                      "render.continuous=my.render.cont,",
                      "overall = NULL)")
  print(eval(parse(text = text2eval)))
}

########################################
#Thease function below for discriptive table, figures ,etc
#######################################

######DONT FORGET TO CHANGE IF MORE WAVES ARE ADDED!!!!

## Prepare function to get all contacts
get_contacts <- function(data,waves=c(1:current_wave),min.waves=length(waves),include.group = F) {
  
  x <- data
  waves <- levels(x$wave)[waves]
  IDS <- x %>%
    filter(wave %in% waves) %>%
    mutate(wave = droplevels(wave))%>%
    group_by(new_id) %>%
    dplyr::summarise(n_waves = n()) %>%
    filter(n_waves >= min.waves) %>% dplyr::select(new_id) %>% pull
  
  dat <- x %>%
    filter(wave %in% waves) %>%
    mutate(wave = droplevels(wave)) %>%
    filter(new_id %in% IDS)
  
  return(dat)
}



# Prepare function to get random rows. Used to highlight random slopes in spaghetti plot
random_subset <- function(x) {
  id <- sample(1:length(x), length(x)/10, replace=T)
  x[id] <- 1
  x[-id] <- 0
  x <- as.numeric(x)
  return(x)
}

# Function to compute change relative to previous wave
relative.change <- function(x) { c(0,diff(x[1:length(x)],differences=1))}


# Function to prepare spaghetti plots
spaghetti.plot <- function(data,waves=levels(data$wave),relative=F,log=F,alpha=.1,title="only participants with observations in at least two time-points") {

  if(relative == T) {data <- data %>% group_by(new_id) %>% mutate(contacts = relative.change(contacts))}
  
  p <- data %>%
        filter(wave %in% waves) %>%
        mutate(random = as.factor(random_subset(contacts))) %>%
        ggplot(aes(x=wave,y=contacts)) +
        geom_line(aes(group=new_id),alpha=alpha) + 
        geom_point(alpha=alpha) +
        theme(legend.position = "none",
              axis.text.x = element_text(angle = 90)) +
        ggtitle(paste0(title))
  
  if(log==T) {p <- p +   scale_y_log10() + ylab("contacts[logscale]") }
  
  print(p)

}

# Function to prepare boxplots
my.boxplot <- function(x,waves=levels(x$wave),relative=F,log=F,title="only participants with observations in at least two time-points") {

  if(relative == T) {x <- x %>% group_by(new_id) %>% mutate(contacts = relative.change(contacts))}
  
  p <- x %>%
        filter(wave %in% waves) %>%
        ggplot(aes(x=wave,y=contacts)) +
        geom_boxplot() + 
        stat_summary(fun=mean, geom="point", shape=20,col="black",size=1, fill="red",aes(shape="mean")) +
        stat_summary(fun=mean,group=1, geom="line",col="black",size=1,linetype="dashed") +
        theme(legend.position = "none",
              axis.text.x = element_text(angle = 90)) +
        ggtitle(paste0(title))
  
  if(log==T) {p <- p +   scale_y_log10() + ylab("contacts[logscale]") }
  
  print(p)

}


##########################
#### Make UpSet plots ####
##########################


plot.upset <- function(x) {
  
#x <- x %>% filter(contacts>0)

m <- table(x$new_id,x$wave) %>%
  make_comb_mat()

ht <- UpSet(m,
      comb_order = order(comb_size(m),decreasing = T),
      set_order = order(set_size(m)),
      row_names_side = "right",
      right_annotation = NULL,
      comb_col = "#3B3B3B",
      left_annotation = rowAnnotation(
        "Set size" = anno_barplot(set_size(m), 
                                  axis_param = list(direction = "reverse"),
                                  border = FALSE, 
                                  #gp = gpar(fill = mypal,col="white"), 
                                  width = unit(2, "cm")
        )))

print(ht)

}


###############################
#### Mean change over time ####
###############################
library(boot)

#sample_mean <- function(x,i) {
#  return(mean(x[i]))
#}

sample_mean <- function(x,i,j) {
  d <- x[i]
  w <- j[i]
  return(weighted.mean(d,w))
}

boot_mean <- function(x,w) {
  set.seed(1234567)
  bo <- boot(x,sample_mean,R=1000,j=w)
  ci <- boot.ci(bo, conf=0.95,type="perc")
  out <- data.frame("mean" = bo$t0,
              "lower" = ci$perc[4],
              "upper" = ci$perc[5])
  return(out)
}

plot.mean <- function(x,waves=levels(x$wave),weighted=F,R=1000,title="Bootstraped mean value with 95% percentile CI - R = 1000 ") {

if(weighted==T) {
plot_df <- x %>%
  filter(wave %in% waves) %>%
  dplyr::group_by(wave) %>%
  do(boot_mean(.$contacts,w=.$weight)) %>%
  ungroup 
} else {
plot_df <- x %>%
  filter(wave %in% waves) %>%
  dplyr::group_by(wave) %>%
  do(boot_mean(.$contacts,w=rep(1,nrow(x)))) %>%
  ungroup  
  
}
}

n_overall.table <- function(x) {
  table(x) %>% as_tibble() %>% rename("Number of waves" = x, "Number of participants" = n) %>% t() %>% kable %>% kable_styling()
}

n.table <- function(x) {
  table(x) %>% as_tibble() %>% rename(Wave = x, Observations = n) %>% t() %>% kable %>% kable_styling()
}

```

#wave label

```{r Vectors to use}
WAVES <- c("30.04.–06.05. (W01)",
           "14.05.–21.05. (W02)",
           "28.05.–04.06. (W03)",
           "11.06.–22.06. (W04)",
           "26.06.–01.07. (W05)",
           "09.07.–16.07. (W06)",
           "24.07.–29.07. (W07)",
           "07.08.–11.08. (W08)",
           "04.09.–09.09. (W09)",
           "30.09.–05.10. (W10)",
           "14.10.–21.10. (W11)",
           "29.10.–03.11. (W12)",
           "05.11.–10.11. (W13)", 
           "25.11.-30.11. (W14)",
           "09.12.-15.12. (W15)",
           "23.12.-30.12. (W16)", 
           "28.01.-02.02. (W17)", 
           "24.02.-03.03. (W18)", 
           "17.03.-26.03. (W19)",
           "07.04.-15.04. (W20)",
           "12.05.-24.05. (W21)",
           "26.05.-03.06. (W22)", 
           "09.06.-22.06. (W23)", 
           "07.07.-19.07. (W24)", 
           "04.08.-13.08. (W25)", 
           "01.09.-14.09. (W26)",
           "22.09.-06.10. (W27)", 
           "08.10.-20.10. (W28)", 
           "22.10.-02.11. (W29)",
           "03.11.-09.11. (W30)", 
           "17.11.-23.11. (W31)",
           "tobe_filled. (W32)")




places <- c("place_home_own",
            "place_home_else",
            "place_work",
            "place_worship",
            "place_transport",
            "place_school",
            "place_shop_essential", 
            "place_shop_non_essential",
            "place_entertainment",
            "place_sport",
            "place_park",
            "place_healthcare",
            "place_beauty",
            "place_oth")
LABEL_PLACES <- c("Own home",
                  "Somebody else's home",
                  "Work",
                  "Worship",
                  "Transport",
                  "School/Uni/Kindergarten",
                  "Essential shopping",
                  "Non-essential shopping",
                  "Entertainment",
                  "Sport",
                  "Park",
                  "Healthcare",
                  "Beauty",
                  "Other",
                  "Not specified",
                  "Multiple locations")
CONTACT_N <- sub("place_", "", places) # delete 'place_' pattern in each element of vector places
CONTACT_N <- paste0(CONTACT_N, "_contact_n")

WEIGHTING <- c("Unweighted", "Weights age & household size")
HH_OUTSIDE <- c()

palette <- c("#003366", "#336699", "#CCFFFF", "#028482", "#663399", "#990033", "#FF3333", "#FF9900", 
             "#266A2E", "#55D43F", "#404040", "#C87533", "#DCDCDC", "#FFDE00", "#F1B2E1", "#FF717E")
# print(palette)
# scales::show_col(palette)

```

# Data overview

Each wave contain 3 datasets: d_self_anonymised, dt_hh_anonymised, dt_outside_anonymised.

##old questionaire

```{r Data information old questionnaire, i.e. wave 1 to 13, results='markup', comment=""}

DATA <- list.files(path = paste0(path_data,"/old_questionnaire"),
                   pattern = "RData",
                   full.names = TRUE)

# all files must have the same structure:
counter <- 0
for(current_file in DATA) {
  counter <- counter + 1
  load(current_file, .GlobalEnv) # , verbose=TRUE)
  WAVE <- current_file
  WAVE <- sub(paste0(path_data,"/old_questionnaire/complete wave "), "", WAVE)
  WAVE <- as.integer(sub("_anonymised[.]RData", "", WAVE))  

  #dataset1:d_self-
  d1 <- as.data.frame(names(d_self_anonymised))
  names(d1) <- "variable"
  d1$wave <- WAVE
  d1$dataset <- "d_self"
  d1$included <- NA_character_
  d_self_anonymised$hh_p_excl_0 <- as.integer(as.character(d_self_anonymised$hh_p_excl_0))
  for(current_column in 1:length(names(d_self_anonymised))) {
    d1$included[current_column] <- paste0(class(d_self_anonymised[, current_column]),collapse = ", ")
  }  
  
  # place_12 = "An einem anderen Ort (bitte angeben)" -> renamed place_oth
  # dt_hh_anonymised$place_12 <- NULL  
  
  d2 <- as.data.frame(names(dt_hh_anonymised))
  names(d2) <- "variable"
  d2$wave <- WAVE
  d2$dataset <- "dt_hh"
  d2$included <- NA_character_
  for(current_column in 1:length(names(dt_hh_anonymised))) {
    d2$included[current_column] <- paste0(class(dt_hh_anonymised[, current_column]),collapse = ", ")
  }  
  
#dataset3:dt_outside
  # place_12 = "An einem anderen Ort (bitte angeben)" -> renamed place_oth
  # dt_outside_anonymised$place_12 <- NULL
  d3 <- as.data.frame(names(dt_outside_anonymised))
  names(d3) <- "variable"
  d3$wave <- WAVE
  d3$dataset <- "dt_outside"
  d3$included <- NA_character_
  for(current_column in 1:length(names(dt_outside_anonymised))) {
    d3$included[current_column] <- paste0(class(dt_outside_anonymised[, current_column]),
                                          collapse = ", ")
  }  
  
  aux <- merge(d1, d2, all = TRUE)
  aux <- merge(aux, d3, all = TRUE)
  aux$n_variable <- dim(d1)[1] # to know how many questions/variables in each wave
  
  if(counter == 1) {
    info_long <- aux
  } else {
    info_long <- merge(info_long, aux, all = TRUE)
  }
  rm(d1, d2, d3, aux, d_self_anonymised, dt_hh_anonymised, dt_outside_anonymised)
}

info_long1 = info_long %>% filter(variable=="age_0")#any variable possible
info_long <- info_long %>% select (-c(n_variable)) # delete n_variable created above
info_wide <- spread(info_long, wave, included)


# write.csv(info_wide,paste0(path_data,"/info_wave_1-13.csv"))

```

##new questionaire

```{r Data information new questionnaire, i.e. wave 14 onwards}

DATA_new <- list.files(path = paste0(path_data,"/new_questionnaire"),
                   pattern = "RData",
                   full.names = TRUE)

# all files must have the same structure:
counter <- 0
for(current_file in DATA_new) {
  counter <- counter + 1
  load(current_file, .GlobalEnv) # , verbose=TRUE)
  WAVE <- current_file
  
  WAVE <- sub(paste0(path_data,"/new_questionnaire/complete wave "), "", WAVE)
  WAVE <- as.integer(sub("_anonymised[.]RData", "", WAVE))
  print(WAVE)
 
  #dataset1: d_self
  d1 <- as.data.frame(names(d_self_anonymised))
  names(d1) <- "variable"
  d1$wave <- WAVE
  d1$dataset <- "d_self"
  d1$included <- NA_character_
  for(current_column in 1:length(names(d_self_anonymised))) {
    d1$included[current_column] <- paste0(class(d_self_anonymised[, current_column]),
                                          collapse = ", ")
  }
  
  

  #dataset2:dt_hh
  dt_hh_anonymised$place_12 <- NULL # to be deleted?
  d2 <- as.data.frame(names(dt_hh_anonymised))
  names(d2) <- "variable"
  d2$wave <- WAVE
  d2$dataset <- "dt_hh"
  d2$included <- NA_character_
  for(current_column in 1:length(names(dt_hh_anonymised))) {
    d2$included[current_column] <- paste0(class(dt_hh_anonymised[, current_column]),collapse = ", ")
  }
  

  
  #dataset3:dt_outside_
    # # place_12 = "An einem anderen Ort (bitte angeben)" -> renamed place_oth
  dt_outside_anonymised$place_12 <- NULL
  d3 <- as.data.frame(names(dt_outside_anonymised))
  names(d3) <- "variable"
  d3$wave <- WAVE
  d3$dataset <- "dt_outside"
  d3$included <- NA_character_
  for(current_column in 1:length(names(dt_outside_anonymised))) {
    d3$included[current_column] <- paste0(class(dt_outside_anonymised[, current_column]),collapse = ", ")
  }
  
  aux <- merge(d1, d2, all = TRUE)
  aux <- merge(aux, d3, all = TRUE)
  aux$n_variable <- dim(d1)[1] # to know how many questions/variables in each wave
  
  if(counter == 1) {
    info_long_new <- aux
  } else {
    info_long_new <- merge(info_long_new, aux, all = TRUE)
  }
  rm(d1, d2, d3, aux, d_self_anonymised, dt_hh_anonymised, dt_outside_anonymised)
}

info_long_new1 = info_long_new %>% filter(variable=="age_0")#any variable possible
info_long_new <- info_long_new %>% select (-c(n_variable)) # delete n_variable created above
info_wide_new <- spread(info_long_new, wave, included)

####
# info_long_all1 <- merge(info_long_new1,info_long1, all = TRUE)
# ggplot(info_long_all1,aes(wave, n_variable))+
#   geom_point()+
#   ggtitle("Number of variables in each wave (d_self dataset)")+
#   theme(plot.title = element_text(face = "bold",hjust = 0.5))

# write.csv(info_wide_new,paste0(path_data,"/info_wave_14-32.csv"))

```

# Merge data and subset to NRW

##wave 1 to 13

```{r Read and merge wave 1 to 13 data, comment="", include=FALSE, results='markup'}
# not the same class across waves:
# contact_id / dt_hh
# contact_id / dt_outside

counter <- 0
for(current_file in DATA) {
  counter <- counter + 1
  load(current_file, .GlobalEnv)
  WAVE <- current_file
  WAVE <- sub(paste0(path_data,"/old_questionnaire/complete wave "), "", WAVE)
  WAVE <- as.integer(sub("_anonymised[.]RData", "", WAVE))  
  
 #dataset1: d_self
  d_self_anonymised$wave <- WAVE
  d_self_anonymised$questionnaire <- "old"

  d_self_anonymised$hh_p_excl_0 <- as.integer(as.character(d_self_anonymised$hh_p_excl_0))
  d_self_anonymised$hh_p_excl_0[which(d_self_anonymised$hh_p_excl_0 > 11)] <- 11 ##hh contact is less likely >11
  d_self_anonymised$contact_id <- as.integer(as.character(d_self_anonymised$contact_id))
  #Q21: hh member name #why it is all 1S
  d_self_anonymised$Q21 <- as.integer(as.character(d_self_anonymised$Q21))# origin is integer
  if(WAVE >= 3) { # new variable in wave 3
    d_self_anonymised$Q74_0 <- as.integer(as.character(d_self_anonymised$Q74_0))
  }
  
  for(current_variable in names(d_self_anonymised)) {
    if(class(d_self_anonymised[, current_variable])[1] %in% c("factor")) { 
      d_self_anonymised[, current_variable] <- as.character(d_self_anonymised[, current_variable])
    }
    if(class(d_self_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      d_self_anonymised[, current_variable] <- as.integer(d_self_anonymised[, current_variable])
    }
  }
  #dataset2:dt_hh
  dt_hh_anonymised$wave <- WAVE
  dt_hh_anonymised$questionnaire <- "old"
  # dt_hh_anonymised$place_12 <- NULL
  
  dt_hh_anonymised$contact_id <- as.double(as.character(dt_hh_anonymised$contact_id))
  for(current_variable in names(dt_hh_anonymised)) {
    if(class(dt_hh_anonymised[, current_variable])[1] %in% c("factor")) { 
      dt_hh_anonymised[, current_variable] <- as.character(dt_hh_anonymised[, current_variable])
    }
    if(class(dt_hh_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      dt_hh_anonymised[, current_variable] <- as.integer(dt_hh_anonymised[, current_variable])
    }
  }
  
  #dataset3:dt_outside
  dt_outside_anonymised$wave <- WAVE
  dt_outside_anonymised$questionnaire <- "old"
  # dt_outside_anonymised$place_12 <- NULL
  
  dt_outside_anonymised$contact_id <- as.integer(as.character(dt_outside_anonymised$contact_id))
  for(current_variable in names(dt_outside_anonymised)) {
    if(class(dt_outside_anonymised[, current_variable])[1] %in% c("factor")) { 
      dt_outside_anonymised[, current_variable] <- as.character(dt_outside_anonymised[, current_variable])
    }
    if(class(dt_outside_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      dt_outside_anonymised[, current_variable] <- as.integer(dt_outside_anonymised[, current_variable])
    }
  }  
  
  # rename datasets and combine all waves
  if(counter == 1) { # first wave
    d_self_all <- d_self_anonymised
    dt_hh_all <- dt_hh_anonymised
    dt_outside_all <- dt_outside_anonymised
  } else { # missing columns will be filled with NA
    d_self_all <- bind_rows(d_self_all, d_self_anonymised)
    dt_hh_all <- bind_rows(dt_hh_all, dt_hh_anonymised)
    dt_outside_all <- bind_rows(dt_outside_all, dt_outside_anonymised)
  }
  rm(d_self_anonymised, dt_hh_anonymised, dt_outside_anonymised)
}

```

##wave 14 to 28

```{r Read and merge wave 14 to 28 data, comment="", include=FALSE, results='markup'}
#not the same class across waves:
# contact_id / dt_hh
# contact_id / dt_outside

counter <- 0
for(current_file in DATA_new) {
  counter <- counter + 1
  load(current_file, .GlobalEnv)
  WAVE <- current_file
  WAVE <- sub(paste0(path_data,"/new_questionnaire/complete wave "), "", WAVE)
  WAVE <- as.integer(sub("_anonymised[.]RData", "", WAVE))  
  
 #dataset1:d_self
  d_self_anonymised$wave <- WAVE
  d_self_anonymised$questionnaire<-"new"
  
  ##class not the same across wave
  for(current_variable in names(d_self_anonymised)) {
    if(class(d_self_anonymised[, current_variable])[1] %in% c("factor")) { 
      d_self_anonymised[, current_variable] <- as.character(d_self_anonymised[, current_variable])
    }
    if(class(d_self_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      d_self_anonymised[, current_variable] <- as.integer(d_self_anonymised[, current_variable])
    }
  }
  
  #dataset2:dt_hh
  dt_hh_anonymised$wave <- WAVE
  dt_hh_anonymised$questionnaire<-"new"
  # dt_hh_anonymised$place_12 <- NULL #why add this variable?
  
  ##class not the same across wave
  dt_hh_anonymised$contact_id <- as.double(as.character(dt_hh_anonymised$contact_id))
  for(current_variable in names(dt_hh_anonymised)) {
    if(class(dt_hh_anonymised[, current_variable])[1] %in% c("factor")) { 
      dt_hh_anonymised[, current_variable] <- as.character(dt_hh_anonymised[, current_variable])
    }
    if(class(dt_hh_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      dt_hh_anonymised[, current_variable] <- as.integer(dt_hh_anonymised[, current_variable])
    }
  }
  
  #dataset3:dt_outside
  dt_outside_anonymised$wave <- WAVE
  dt_outside_anonymised$questionnaire<-"new"
  # dt_outside_anonymised$place_12 <- NULL
  
  ##class not the same across wave
  dt_outside_anonymised$contact_id <- as.integer(as.character(dt_outside_anonymised$contact_id))
  dt_hh_anonymised$contact_id <- as.integer(dt_hh_anonymised$contact_id)#in all data set is numeric, but it does not affect...
  dt_outside_anonymised$contact_id <- as.integer(dt_outside_anonymised$contact_id)
  dt_outside_anonymised$contact <- as.integer(dt_outside_anonymised$contact)
  # why all variables below is NAs?????
  d_self_anonymised$q79a <- as.integer(d_self_anonymised$q79a)
  d_self_anonymised$q79c <- as.integer(d_self_anonymised$q79c)
  d_self_anonymised$Q80a <- as.integer(d_self_anonymised$Q80a)
  d_self_anonymised$Q80c <- as.integer(d_self_anonymised$Q80c)
  d_self_anonymised$Q81a <- as.integer(d_self_anonymised$Q81a)
  d_self_anonymised$Q81c <- as.integer(d_self_anonymised$Q81c)
  d_self_anonymised$Q21_scale <- as.character(d_self_anonymised$Q21_scale)
  
  for(current_variable in names(dt_outside_anonymised)) {
    if(class(dt_outside_anonymised[, current_variable])[1] %in% c("factor")) { 
      dt_outside_anonymised[, current_variable] <- as.character(dt_outside_anonymised[, current_variable])
    }
    if(class(dt_outside_anonymised[, current_variable])[1] %in% c("haven_labelled")) { 
      dt_outside_anonymised[, current_variable] <- as.integer(dt_outside_anonymised[, current_variable])
    }
  }  

skin_integer <- c("skin_skin_to_skin","skin_kept_dist_2m" ,"skin_kept_dist_1m", "skin_dist_less_1m", "skin_wore_mask", "skin_washsan_bef" , "skin_washsan_aft", "skin_prefer_not_to_say", "skin_none_of_these", "skin_dont_know")
  
  
  
    d_self_all <- bind_rows(d_self_all, d_self_anonymised)
    dt_hh_all <- bind_rows(dt_hh_all, dt_hh_anonymised)
    dt_outside_all <- bind_rows(dt_outside_all, dt_outside_anonymised)

  rm(d_self_anonymised, dt_hh_anonymised, dt_outside_anonymised)
}

```

##NRW
Variable: bundesland_0 == "Nordrhein-Westfalen"
d_self_all: 

```{r}
d_self_all<- d_self_all%>%filter(bundesland_0 == "Nordrhein-Westfalen")#upto wave 32:12360 obs
dt_outside_all<-  dt_outside_all[dt_outside_all$new_id %in% d_self_all$new_id, ] # subset NRW
dt_hh_all<- dt_hh_all[dt_hh_all$new_id %in% d_self_all$new_id, ] # subset NRW

# obs_wave_upto32 <- 1560+1356+1081+1890+1615+1496+1207+1022+869+739+1499+1500+1500+1490+1500+1499+997+1499+1498+1493+2468+2441+2485+2468+2480+2502+2492+2493+2487+2487+2489+2490 # 32 wave


```


# Translate group contacts

Q75: Wave 3-13

Q79: Wave 14- onward

This code below to integrate group contact information across waves into Q.75 style. 

The missing answer in this question is very high (>85%). The possible reason is the respondent answered the individual contact question and don't care much about this question anymore.

*The missing mean not giving answer ?

```{r results="asis"}
# names wave 3-13   new names wave 14 onwards
# Q75_u18_work	    Q79_age_met_work_u18
# Q75_1864_work	    Q79_age_met_work_1864
# Q75_o64_work	    Q79_age_met_work_o64
# Q75_u18_school  	Q80a_age_met_uni_u18
# Q75_1864_school 	Q80a_age_met_uni_1864
# Q75_o64_school  	Q80a_age_met_uni_o64
# Q75_u18_else	    Q81a_age_met_else_u18
# Q75_1864_else	    Q81a_age_met_else_1864
# Q75_o64_else    	Q81a_age_met_else_o64
# Q76_u18_work    	Q79c_age_phys_work_u18
# Q76_1864_work   	Q79c_age_phys_work_1864
# Q76_o64_work    	Q79c_age_phys_work_o64
# Q76_u18_school  	Q80c_age_phys_uni_u18
# Q76_1864_school 	Q80c_age_phys_uni_1864
# Q76_o64_school  	Q80c_age_phys_uni_o64
# Q76_u18_else	    Q81c_age_phys_else_u18
# Q76_1864_else	    Q81c_age_phys_else_1864
# Q76_o64_else	    Q81c_age_phys_else_o64


d_self_all <- d_self_all %>% mutate (Q75_u18_work = ifelse(questionnaire=="new", Q79a_age_met_work_u18, Q75_u18_work))
d_self_all <- d_self_all %>% mutate (Q75_1864_work = ifelse(questionnaire=="new", Q79a_age_met_work_1864, Q75_1864_work))
d_self_all <- d_self_all %>% mutate (Q75_1864_work = ifelse(questionnaire=="new", Q79a_age_met_work_o64, Q75_o64_work))
d_self_all <- d_self_all %>% mutate (Q75_u18_school = ifelse(questionnaire=="new", Q80a_age_met_uni_u18, Q75_u18_school))
d_self_all <- d_self_all %>% mutate (Q75_1864_school = ifelse(questionnaire=="new", Q80a_age_met_uni_1864, Q75_1864_school))
d_self_all <- d_self_all %>% mutate (Q75_o64_school = ifelse(questionnaire=="new", Q80a_age_met_uni_o64, Q75_o64_school))
d_self_all <- d_self_all %>% mutate (Q75_u18_else = ifelse(questionnaire=="new", Q81a_age_met_else_u18, Q75_u18_else))
d_self_all <- d_self_all %>% mutate (Q75_1864_else = ifelse(questionnaire=="new", Q81a_age_met_else_1864, Q75_1864_else))
d_self_all <- d_self_all %>% mutate (Q75_o64_else = ifelse(questionnaire=="new", Q81a_age_met_else_o64, Q75_o64_else))
d_self_all <- d_self_all %>% mutate (Q76_u18_work = ifelse(questionnaire=="new", Q79c_age_phys_work_u18, Q76_u18_work))
d_self_all <- d_self_all %>% mutate (Q76_1864_work = ifelse(questionnaire=="new", Q79c_age_phys_work_1864, Q76_1864_work))
d_self_all <- d_self_all %>% mutate (Q76_o64_work = ifelse(questionnaire=="new", Q79c_age_phys_work_o64, Q76_o64_work))
d_self_all <- d_self_all %>% mutate (Q76_u18_school = ifelse(questionnaire=="new", Q80c_age_phys_uni_u18, Q76_u18_school))
d_self_all <- d_self_all %>% mutate (Q76_1864_school = ifelse(questionnaire=="new", Q80c_age_phys_uni_1864, Q76_1864_school))
d_self_all <- d_self_all %>% mutate (Q76_o64_school = ifelse(questionnaire=="new", Q80c_age_phys_uni_o64, Q76_o64_school))
d_self_all <- d_self_all %>% mutate (Q76_u18_else = ifelse(questionnaire=="new", Q81c_age_phys_else_u18, Q76_u18_else))
d_self_all <- d_self_all %>% mutate (Q76_1864_else = ifelse(questionnaire=="new", Q81c_age_phys_else_1864, Q76_1864_else))
d_self_all <- d_self_all %>% mutate (Q76_o64_else = ifelse(questionnaire=="new", Q81c_age_phys_else_o64, Q76_o64_else))

# sumary table 
table1(~Q75_u18_work + Q75_1864_work + Q75_1864_work +
       Q75_u18_school + Q75_1864_school+ Q75_o64_school + Q75_u18_else +Q75_1864_else +Q75_o64_else | as.factor(wave), data=d_self_all)
  
```

# Remove work contacts from <15 year olds
The respondent < 15 year-old should not have work contact. Therefore, the work contact with those individuals (if any) should set to 0.

```{r results="asis"}

#In each wave, each participant (new_id) should be unique, check if it is true.
for (w in 1:current_wave){
  wave<- d_self_all %>% filter(wave==w)
  if(dim(wave)[1] !=  length(unique(wave$new_id))){
    print(paste0("Warning_new_id is not unique in wave",w))
  }
}

#Set the work contacts of the < 15 year olds to 0
dummy <- d_self_all %>% select(new_id, wave, age_group)
dummynames<-c("new_id", "wave","age_group_participant")
colnames(dummy) <- dummynames
dummy <- merge(dummy, dt_outside_all, by=c("new_id", "wave"), all.y =T) # number of obs should be the same as the largest dataset because only new cols (y) will be added
dummy$place_work[(dummy$age_group_participant=="Under 1" | 
                    dummy$age_group_participant=="1-4" |
                    dummy$age_group_participant=="5-9" | 
                    dummy$age_group_participant=="10-14") & 
                    dummy$place_work==1 ] <- 0

dt_outside_all <- dummy %>% select(-c(age_group_participant))

rm(dummy)

```

# Count multiple contact

place_.. variable is not consistent in format:

- most of variables are labeled ["Yes","No","NA], but **place_oth** contain[ NA, "1"].
=> should we replace place_oth by place_12 ? 

But, in the non_hh_contact_number function, the variable used is place_oth and the format used is correct. So this shouldn't be a problem!

**place_multiple**: 1 = 'Yes', 0 = 'No


```{r }

# hh data
dt_hh_all <- dt_hh_all %>% dplyr::mutate(place_multiple = rowSums(select(.,place_home_own:place_oth) == "Yes", na.rm=TRUE))

table(dt_hh_all$place_multiple)

#this code convert...to binary value: 0 (No), 1(Yes)
#Veronika's version is integer
dt_hh_all$place_multiple <- as.factor(as.integer(dt_hh_all$place_multiple >= 2))# if place_multiple >- 2 -> assign to 1 ( Yes), otherwise 0 (No)

table(dt_hh_all$place_multiple)

# non_hh data
dt_outside_all <- dt_outside_all %>% dplyr::mutate(place_multiple = rowSums(select(.,place_home_own:place_oth) == "Yes", na.rm=TRUE))

table(dt_outside_all$place_multiple)

dt_outside_all$place_multiple <- as.factor(as.integer(dt_outside_all$place_multiple >= 2))

table(dt_outside_all$place_multiple)

```

# Summary tables
## contacts per ID and wave

**These variables below are non_hh_contact**

place_home_own                       -> **home_own_contact_n**

place_home_else                      -> **home_else_contact_n**

place_work-> simmilar pattern

place_worship

place_transport

place_school

place_shop_essential

place_shop_non_essential

place_entertainment (e.g. restaurant, bar/pub, cinema)

place_sport

place_park

place_healthcare

place_beauty

place_oth 

**not_specified_contact_n** : the respondent did not chose any place above, except place_oth (i.e.the respondent ["27e7cde0"
, wave 23] report 15 contacts, 1 is place_oth_n => not_specified_contact_n is 14 )

**leisure_contact_n* : contact at either home_own|home_else|worship|shop_non_essential|entertainment|sport|park|beauty

**other_combined_contact_n** ( the reast places) includes transport|healthcare|shop_essential|place_oth

**all_contact_n** includes hh_contacts_n and non_hh_contact_n

**all_contact_n_inside** includes hh_contacts_n and non_hh_contact_n inside

**all_contact_n_outside** includes hh_contacts_n and non_hh_contact_n outside

*work and school are not grouped into these variables

- It is possible that a respondent meet the same person at different places (i.e: meet at bar, and then go home together [ wave 6, 004eff99: non_hh_contact_n is 2 ,but has 1 home_own_contact_n
 and 2 entertainment_contact_n
])

* merge function: all = T  => "More rows than expected!" (59 more rows added). So, I set all.x =T instead. The number of row now is equal.

But, this raise a concern about data set

a <- d_self_all%>% filter (new_id == "2d403424")-> 1 result

a1 <- hh_contacts%>% filter (new_id == "2d403424") -> 8 results

Similar new_id: 221715af, 309e56ad, 59793b54,71c9e526,....

```{r }
# All contacts (inside and outside)
## Function used here can be found in function chunk
hh_contacts <- hh_contact_number(dt_hh_all, new_id, wave)
outside_contacts <- non_hh_contact_number(dt_outside_all, new_id, wave)

nrow(d_self_all)
nrow(hh_contacts)      # must be <= nrow(d_self_all)
nrow(outside_contacts) # must be <= nrow(d_self_all)

#create new_id_wave contain new_id and wave information. This should be unique in d_self_all, hh_contacts , and  outside_contacts dataset.All new_id_wave in hh_contacts and  outside_contacts should be in d_self_all. Check if this true!
hh_contacts$new_id_wave <- paste0(hh_contacts$new_id,"_",hh_contacts$wave)
outside_contacts$new_id_wave <- paste0(outside_contacts$new_id,"_",outside_contacts$wave)
d_self_all$new_id_wave <- paste0(d_self_all$new_id,"_",d_self_all$wave)
#checking
a <- summary(hh_contacts$new_id_wave %in% d_self_all$new_id_wave)
if (a[[3]] != dim(hh_contacts)[1]){
  print("Warning:some unique id (new_id & wave) in hh_contact may not be in d_sell_all")
}
b <- summary(outside_contacts$new_id_wave %in% d_self_all$new_id_wave)
if (a[[3]] != dim(outside_contacts)[1]){
  print("Warning:some unique id (new_id & wave) in outside_contacts may not be in d_sell_all")
}
rm(a,b)

# # subset to see what make the difference (if any)
# ##switch on when further investigation needed
# hh_contacts_diff <- hh_contacts[which(hh_contacts$new_id_wave %in% d_self_all$new_id_wave==FALSE),]
# outside_contacts_diff <- outside_contacts[which(outside_contacts$new_id_wave %in% d_self_all$new_id_wave==FALSE),]
# a <- d_self_all%>% filter (new_id == "71c9e526")
# a1 <- hh_contacts%>% filter (new_id == "71c9e526")


#integrate dataset

d_all_wide <- merge(d_self_all, hh_contacts, by=c("new_id", "wave"), all.x =T) 
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, outside_contacts, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }


# Inside contacts
aux_hh <- dt_hh_all %>% filter(place_inside=="Yes") #1 = Yes, 0=No
hh_contacts <- hh_contact_number(aux_hh, new_id, wave)

aux_outside <- dt_outside_all %>% filter(place_inside=="No")
outside_contacts <- non_hh_contact_number(aux_outside, new_id, wave)

nrow(d_self_all)
nrow(hh_contacts)      # must be <= nrow(d_self_all)
nrow(outside_contacts) # must be <= nrow(d_self_all)

# rename
names(hh_contacts) <- sub("_contact_n", "_contact_n_inside", names(hh_contacts))
names(outside_contacts) <- sub("_contact_n", "_contact_n_inside", names(outside_contacts))

d_all_wide <- merge(d_all_wide, hh_contacts, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, outside_contacts, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }

names(d_all_wide)


# Outside contacts
aux_hh <- dt_hh_all %>% filter(place_outside=="Yes")#1 = Yes, 0=No
hh_contacts <- hh_contact_number(aux_hh, new_id, wave)

aux_outside <- dt_outside_all %>% filter(place_outside=="NO")
outside_contacts <- non_hh_contact_number(aux_outside, new_id, wave)

nrow(d_self_all)
nrow(hh_contacts)      # must be <= nrow(d_self_all)
nrow(outside_contacts) # must be <= nrow(d_self_all)

# rename
names(hh_contacts) <- sub("_contact_n", "_contact_n_outside", names(hh_contacts))
names(outside_contacts) <- sub("_contact_n", "_contact_n_outside", names(outside_contacts))

d_all_wide <- merge(d_all_wide, hh_contacts, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) < nrow(d_self_all)) { message("Less rows than expected!") }
d_all_wide <- merge(d_all_wide, outside_contacts, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) < nrow(d_self_all)) { message("Less rows than expected!") }

# any NA in _contact_n means zero contacts in that setting
for(current_variable in names(d_all_wide)[grep("contact_n", names(d_all_wide))]) {
  d_all_wide[is.na(d_all_wide[, current_variable]), current_variable] <- 0
}


# all contacts
d_all_wide$all_contact_n <- 
  d_all_wide$hh_contact_n + d_all_wide$non_hh_contact_n

d_all_wide$all_contact_n_inside <- 
  d_all_wide$hh_contact_n_inside + d_all_wide$non_hh_contact_n_inside

d_all_wide$all_contact_n_outside <- 
  d_all_wide$hh_contact_n_outside + d_all_wide$non_hh_contact_n_outside


#################################################################################################
#################################################################################################
# Contact duration in non-hh contacts for bar chart
#first categorise
dt_outside_all$contact_duration_minutes <- dt_outside_all$time_hh * 60 + dt_outside_all$time_mm
dt_outside_all$contact_duration_minutes[which(dt_outside_all$contact_duration_minutes > 24 * 60)] <- 24 * 60
dt_outside_all$contact_duration_minutes_cat[dt_outside_all$contact_duration_minutes<5]<-"<5"
dt_outside_all$contact_duration_minutes_cat[dt_outside_all$contact_duration_minutes>4 & dt_outside_all$contact_duration_minutes<15]<-">=5 & <15"
dt_outside_all$contact_duration_minutes_cat[dt_outside_all$contact_duration_minutes>14 & dt_outside_all$contact_duration_minutes<60]<-">=15 & <60"
dt_outside_all$contact_duration_minutes_cat[dt_outside_all$contact_duration_minutes>59 & dt_outside_all$contact_duration_minutes<240]<-">=60 & <240"
dt_outside_all$contact_duration_minutes_cat[dt_outside_all$contact_duration_minutes>239]<-">=240"

dt_outside_all$contact_duration_minutes_cat <- as.character(dt_outside_all$contact_duration_minutes_cat, levels = c('<5','>=5 & <15','>=15 & <60','>=60 & <240','>=240'))


# from wave 14 onwards contact duration is recorded as Less than 5 minutes, etc. Need to take the values of the variable ""
dt_outside_all$con_time[dt_outside_all$con_time=="Less than 5 minutes"] <- "<5"
dt_outside_all$con_time[dt_outside_all$con_time==" Less than 5 minutes"] <- "<5"
dt_hh_all$con_time[dt_hh_all$con_time=="Less than 5 minutes"] <- "<5"
dt_hh_all$con_time[dt_hh_all$con_time==" Less than 5 minutes"] <- "<5"
dt_outside_all$con_time[dt_outside_all$con_time=="5 minutes or more, but less than 15 minutes"] <- ">=5 & <15"
dt_hh_all$con_time[dt_hh_all$con_time=="5 minutes or more, but less than 15 minutes"] <- ">=5 & <15"
dt_outside_all$con_time[dt_outside_all$con_time=="15 minutes or more, but less than 1 hour"] <- ">=15 & <60"
dt_hh_all$con_time[dt_hh_all$con_time=="15 minutes or more, but less than 1 hour"] <- ">=15 & <60"
dt_outside_all$con_time[dt_outside_all$con_time=="1 hour or more, but less than 4 hours"] <- ">=60 & <240"
dt_hh_all$con_time[dt_hh_all$con_time=="1 hour or more, but less than 4 hours"] <- ">=60 & <240"
dt_outside_all$con_time[dt_outside_all$con_time=="4 hours or more"] <- ">=240"
dt_hh_all$con_time[dt_hh_all$con_time=="4 hours or more"] <- ">=240"
dt_outside_all$con_time[dt_outside_all$con_time=="Don’t know"] <- NA
dt_hh_all$con_time[dt_hh_all$con_time=="Don’t know"] <- NA


#merge contact_duration_mininutes (before wave 13) and con_time (wave 14 onward)
dt_outside_all <- dt_outside_all %>% mutate (contact_duration_minutes_cat = case_when(questionnaire=="new" ~ con_time, TRUE ~ contact_duration_minutes_cat))



dummy_0_4 <- dt_outside_all %>% 
  filter(contact_duration_minutes_cat=="<5") %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(non_hh_duration_0_4_contact_n=n())

dummy_5_14 <- dt_outside_all %>% 
  filter(contact_duration_minutes_cat==">=5 & <15") %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(non_hh_duration_5_14_contact_n=n())

dummy_15_59 <- dt_outside_all %>% 
  filter(contact_duration_minutes_cat==">=15 & <60") %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(non_hh_duration_15_59_contact_n=n())

dummy_60_239 <- dt_outside_all %>% 
  filter(contact_duration_minutes_cat==">=60 & <240") %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(non_hh_duration_60_239_contact_n=n())

dummy_240 <- dt_outside_all %>% 
  filter(contact_duration_minutes_cat==">=240") %>% 
  group_by(new_id, wave) %>% 
  dplyr::summarise(non_hh_duration_240_contact_n=n())


# merge with d_all_wide
d_all_wide <- merge(d_all_wide, dummy_0_4, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, dummy_5_14, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, dummy_15_59, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, dummy_60_239, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
d_all_wide <- merge(d_all_wide, dummy_240, by=c("new_id", "wave"), all.x=T)
if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }


# any NA in _contact_n means zero contacts in that setting
for(current_variable in names(d_all_wide)[grep("contact_n", names(d_all_wide))]) {
  d_all_wide[is.na(d_all_wide[, current_variable]), current_variable] <- 0
}

rm(dummy_0_4, dummy_5_14, dummy_15_59, dummy_60_239, dummy_240)
#################################################################################################
#################################################################################################


# 
# ###WORK IN PROGRESS
# #################################################################################################
# #relation for bar chart
# # combine relation and relation_child (wave 14 onwards)
# dt_outside_all$relation_2 <- dt_outside_all$relation
# dt_outside_all <- dt_outside_all %>% mutate(relation_2 = case_when(is.na(relation) ~ relation_child, TRUE ~ relation))
# 
# dt_outside_all$relation_2[dt_outside_all$relation_2=="School/Uni"] <- "School"
# dt_outside_all$relation_2[dt_outside_all$relation_2=="Kindergarden/School/Uni"] <- "School"
# dt_outside_all$relation_2[dt_outside_all$relation_2=="Spouse/Significant other"] <- "Family (not in household)"
# dt_outside_all$relation_2[dt_outside_all$relation_2=="Babysitter"] <- "Other"
# dt_outside_all$relation_2[dt_outside_all$relation_2=="Client"] <- "Other"
# dt_outside_all$relation_2[dt_outside_all$relation_2=="Don't want to answer" | dt_outside_all$relation_2=="Prefer not to answer" | dt_outside_all$relation_2=="Prefer not to say"] <- NA
# 
# ###### CAVE Still need to adapt once we also have the relation of children, i.e. QP question
# #### NEED TO UPDATE WORK IN PROGRESS
# 
# 
# # Contact relation in non-hh contacts
# relation_family <- dt_outside_all %>%
#   filter(relation_2=="Family (not in household)") %>%
#   group_by(new_id, wave) %>%
#   summarise(non_hh_relation_family_contact_n=n())
# 
# relation_friend <- dt_outside_all %>%
#   filter(relation_2=="Friend") %>%
#   group_by(new_id, wave) %>%
#   summarise(non_hh_relation_friend_contact_n=n())
# 
# relation_other <- dt_outside_all %>%
#   filter(relation_2=="Other") %>%
#   group_by(new_id, wave) %>%
#   summarise(non_hh_relation_other_contact_n=n())
# 
# relation_school <- dt_outside_all %>%
#   filter(relation_2=="School") %>%
#   group_by(new_id, wave) %>%
#   summarise(non_hh_relation_school_contact_n=n())
# 
# relation_work <- dt_outside_all %>%
#   filter(relation_2=="Work") %>%
#   group_by(new_id, wave) %>%
#   summarise(non_hh_relation_work_contact_n=n())
# 
# 
# # merge with d_all_wide
# d_all_wide <- merge(d_all_wide, relation_family, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, relation_friend, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, relation_other, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, relation_school, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, relation_work, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# 
# 
# # any NA in _contact_n means zero contacts in that setting
# for(current_variable in names(d_all_wide)[grep("contact_n", names(d_all_wide))]) {
#   d_all_wide[is.na(d_all_wide[, current_variable]), current_variable] <- 0
# }
# 
# rm(relation_family, relation_friend, relation_other, relation_school, relation_work)
# 
# table1::table1(~non_hh_relation_family_contact_n + non_hh_relation_friend_contact_n + non_hh_relation_other_contact_n + non_hh_relation_school_contact_n + non_hh_relation_work_contact_n | wave, data=d_all_wide)
# 
# #################################################################################################
# #################################################################################################
# 
# 
# 
# 
# #################################################################################################
# #how often before COVID for bar chart
# dt_outside_all$time_before_COV_2 <- dt_outside_all$time_before_COV
# dt_outside_all$time_before_COV_2[dt_outside_all$time_before_COV=="Prefer not to answer" | dt_outside_all$time_before_COV=="Don’t know"] <- NA
# 
# # How regularly met before COVID in non-hh contacts
# before_once_week <- dt_outside_all %>% 
#   filter(time_before_COV_2=="About once or twice a week") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_onceweek_contact_n=n())
# 
# before_once_month <- dt_outside_all %>% 
#   filter(time_before_COV_2=="About once per month") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_oncemonth_contact_n=n())
# 
# before_2_weeks <- dt_outside_all %>% 
#   filter(time_before_COV_2=="Every 2-3 weeks") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_2weeks_contact_n=n())
# 
# before_every_day <- dt_outside_all %>% 
#   filter(time_before_COV_2=="Every day or almost every day") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_everyday_contact_n=n())
# 
# before_less_month <- dt_outside_all %>% 
#   filter(time_before_COV_2=="Less often than once per month") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_lessmonth_contact_n=n())
# 
# before_never <- dt_outside_all %>% 
#   filter(time_before_COV_2=="Never met them before") %>% 
#   group_by(new_id, wave) %>% 
#   dplyr::summarise(non_hh_before_never_contact_n=n())
# 
# 
# # merge with d_all_wide
# d_all_wide <- merge(d_all_wide, before_once_week, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, before_once_month, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, before_2_weeks, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, before_every_day, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, before_less_month, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# d_all_wide <- merge(d_all_wide, before_never, by=c("new_id", "wave"), all.x=T)
# if(nrow(d_all_wide) != nrow(d_self_all)) { message("More rows than expected!") }
# 
# # any NA in _contact_n means zero contacts in that setting
# for(current_variable in names(d_all_wide)[grep("contact_n", names(d_all_wide))]) {
#   d_all_wide[is.na(d_all_wide[, current_variable]), current_variable] <- 0
# }
# 
# rm(before_once_week, before_once_month, before_2_weeks, before_every_day, before_less_month, before_never)
# 
# table1::table1(~non_hh_before_onceweek_contact_n + non_hh_before_oncemonth_contact_n + non_hh_before_2weeks_contact_n + non_hh_before_everyday_contact_n + non_hh_before_lessmonth_contact_n + non_hh_before_never_contact_n | wave, data=d_all_wide)




```


##create weekday
The contact is recorded one day before report day. so, the weekday of contact is counted from Tuesday to Saturday next week, and weekend is Sunday and Monday next week.

```{r }
d_all_wide$date <- ymd(paste0(d_all_wide$date_YYYY_0, "/", d_all_wide$date_MM_0, "/", d_all_wide$date_DD_0))
d_all_wide$weekday <- lubridate::wday(d_all_wide$date, week_start = 7) # week starts on Sunday
d_all_wide$weekday <- factor(d_all_wide$weekday, labels = c("Sun", "Mon", "Tue", "Wed","Thu", "Fri", "Sat"))
d_all_wide$weekday <- factor(d_all_wide$weekday, levels = c("Mon", "Tue", "Wed","Thu", "Fri", "Sat", "Sun"))

 # table(d_all_wide$date, d_all_wide$weekday)
 
#weekday for which contacts recorded, i.e. weekday - 1
 d_all_wide$weekday_2[d_all_wide$weekday=="Mon"] <- "Sun"
 d_all_wide$weekday_2[d_all_wide$weekday=="Tue"] <- "Mon"
 d_all_wide$weekday_2[d_all_wide$weekday=="Wed"] <- "Tue"
 d_all_wide$weekday_2[d_all_wide$weekday=="Thu"] <- "Wed"
 d_all_wide$weekday_2[d_all_wide$weekday=="Fri"] <- "Thu"
 d_all_wide$weekday_2[d_all_wide$weekday=="Sat"] <- "Fri"
 d_all_wide$weekday_2[d_all_wide$weekday=="Sun"] <- "Sat"
 d_all_wide$weekday_2 <- factor(d_all_wide$weekday_2, levels=c("Mon","Tue","Wed","Thu", "Fri", "Sat", "Sun"))
 d_all_wide$weekend_weekday[d_all_wide$weekday_2=="Mon" | d_all_wide$weekday_2=="Tue" |  d_all_wide$weekday_2=="Wed" |  d_all_wide$weekday_2=="Thu" | d_all_wide$weekday_2=="Fri"] <- "weekday"
 d_all_wide$weekend_weekday[d_all_wide$weekday_2=="Sat" | d_all_wide$weekday_2=="Sun"] <- "weekend"
 
 table(d_all_wide$date, d_all_wide$weekend_weekday)

 
```

## Age group
```{r results="asis"}
d_all_wide$age_group[which(d_all_wide$age_group == "Under 1")] <- "<1"
# table(d_all_wide$age_group, d_all_wide$wave_0)
table1::table1(~age_group| wave, data=d_all_wide)

```


## Sex

```{r results="asis"}

# age groups
# from wave 14 onwards a category exists 85 years or older => put into 85+
d_all_wide$age_group[d_all_wide$age_group=="85 years or older"] <- "85+"

#groups <- sort(unique(d_all_wide$age_group))
#groups <- setdiff(groups,c("Don’t know","Prefer not to answer","<1"))
d_all_wide$age_group_2[d_all_wide$age_group=="Under 1" | d_all_wide$age_group=="1-4" | d_all_wide$age_group=="5-9"| d_all_wide$age_group=="10-14" | d_all_wide$age_group=="15-19"] <- "0-19"
d_all_wide$age_group_2[d_all_wide$age_group=="20-24" | d_all_wide$age_group=="25-34" ] <- "20-34"
d_all_wide$age_group_2[d_all_wide$age_group=="35-44" | d_all_wide$age_group=="45-54"] <- "35-54"
d_all_wide$age_group_2[ d_all_wide$age_group=="55-64" ] <- "55-64"
d_all_wide$age_group_2[ d_all_wide$age_group=="65-69"] <- "65-69"
d_all_wide$age_group_2[ d_all_wide$age_group=="70-74" | d_all_wide$age_group=="75-79" | d_all_wide$age_group=="80-84" | d_all_wide$age_group=="85+"] <- "70+"

#sex2
# only keep Female and  Male , the rest ( i.e : "In another way", "Prefer not to answer") become NA
d_all_wide$sex2 [d_all_wide$sex=="Female"] <- "Female"
d_all_wide$sex2[d_all_wide$sex=="Male"] <- "Male"


table1::table1(~ sex2 | as.factor(wave), data=d_all_wide)


```

## hh size 

```{r results="asis"}

#####CAVE, CAVE, CAVE - there is still an issue with wave 14. hh_p_incl_0 ranges from 0 to 11 instead of 1 to 12. Email to Sara send.
# household size
#wave 14 onwards already has variable hh_p_incl_0 => must add 1 to hh_p_excl_0 from waves 1 to 13
d_all_wide <- d_all_wide %>% mutate(hh_p_incl_0 = ifelse(questionnaire=="old", (hh_p_excl_0+1), hh_p_incl_0))
d_all_wide <- d_all_wide %>% mutate(hh_p_incl_0 = ifelse(wave==14, (hh_p_incl_0+1), hh_p_incl_0))

#hh size
table1::table1(~hh_p_incl_0 + as.factor(hh_p_incl_0) | as.factor(wave), data=d_all_wide)

d_all_wide$hh_p_incl_0_2[d_all_wide$hh_p_incl_0=="1"] <- "1"
d_all_wide$hh_p_incl_0_2[d_all_wide$hh_p_incl_0>1 & d_all_wide$hh_p_incl_0<5] <- "2-4"
d_all_wide$hh_p_incl_0_2[d_all_wide$hh_p_incl_0>4 & d_all_wide$hh_p_incl_0<10] <- "5-9"
d_all_wide$hh_p_incl_0_2[d_all_wide$hh_p_incl_0>9] <- "10+"
d_all_wide$hh_p_incl_0_2 <- factor(d_all_wide$hh_p_incl_0_2, levels=c("1","2-4","5-9","10+"))

d_all_wide$hh_p_incl_0_3[d_all_wide$hh_p_incl_0=="1"] <- "1"
d_all_wide$hh_p_incl_0_3[d_all_wide$hh_p_incl_0==2] <- "2"
d_all_wide$hh_p_incl_0_3[d_all_wide$hh_p_incl_0>2 & d_all_wide$hh_p_incl_0<6] <- "3-5"
d_all_wide$hh_p_incl_0_3[d_all_wide$hh_p_incl_0>5] <- "6+"
d_all_wide$hh_p_incl_0_3 <- factor(d_all_wide$hh_p_incl_0_3, levels=c("6+","3-5","2","1"))


```


## Age, sex, and hh size
```{r results="asis"}
# label for the table
table1::label(d_all_wide$sex2)<-"Sex"
#label(df$weekend_weekday)<-"Weekday/Weekend"
table1::label(d_all_wide$age_group_2)<-"Age in years"
table1::label(d_all_wide$hh_p_incl_0_2)<-"Household size"

table1(~ age_group_2 + sex2 +hh_p_incl_0_2|wave, data=d_all_wide)

```

## add Q75/76
Q.75 How many people have you had contact with whom you did not specify individually? Please, provide an estimated value as precisely as possible, including age and environment. For the purpose of this question, we are only interested in people with whom there was direct contact and with whom you have exchanged at least a few words OR with whom you have had physical contact (e.g. shaking hands, hugging, contact sports). Please, indicate the number of contacts for each age group and each environment.

Q.76 Roughly how many people did you have phyiscal contact (body contact) with that you did not specify individually? Please, provide an estimated value as precisely as possible, including age and environment. For the purpose of this question, we are only interested in people who have had direct contact AND with whom you have had physical contact (e.g. shaking hands, hugging, contact sports). Please, indicate the number of contacts for each age group and each environment.

????
The group contact info mainly retrieved from Q75.However, if Q76 > Q75 -> use Q76 


```{r Add Q75 / Q76 contacts AND truncate Q contacts at 50}
# Please check each category individually. I.e. compare Q75_u18_work with Q76_u18_work and replace if necessary and that just for each category. That's how I did it so far and Victoria took over from me.


# Please indicate the number of contacts for each age group and setting.
# ROWS
# Under 18 years 
# 18 to 64 years
# 65 years and older
# COLUMNS.
# Am Arbeitsplatz -> add to work_contact_n (no info about inside/outside!)
v <- which(d_all_wide$Q76_u18_work > d_all_wide$Q75_u18_work)#index rows that ...bigger, how about smaller => should we use !=????
d_all_wide$Q75_u18_work[v] <- d_all_wide$Q76_u18_work[v]

v <- which(d_all_wide$Q76_1864_work > d_all_wide$Q75_1864_work)
d_all_wide$Q75_1864_work[v] <- d_all_wide$Q76_1864_work[v]

v <- which(d_all_wide$Q76_o64_work > d_all_wide$Q75_o64_work)
d_all_wide$Q75_o64_work[v] <- d_all_wide$Q76_o64_work[v]

#work contact

d_all_wide$Q75_work_sum <- rowSums(d_all_wide[, c("Q75_u18_work",
                                                  "Q75_1864_work",
                                                  "Q75_o64_work")],
                                   na.rm = TRUE)


## < 15 yrs old -> no work contact
d_all_wide$Q75_work_sum[d_all_wide$age_group=="Under 1" | 
                          d_all_wide$age_group=="1-4" |
                          d_all_wide$age_group=="5-9" |
                          d_all_wide$age_group=="10-14"] <- 0


##truncate at "truncate" before adding to work contacts
d_all_wide$Q75_work_sum[d_all_wide$Q75_work_sum > truncate] <- truncate

## add the work Q contacts to the overall work contacts
d_all_wide$work_contact_n_Q75 <- d_all_wide$work_contact_n + d_all_wide$Q75_work_sum



# In der Schule oder einer anderen Lehranstalt -> add to school_contact_n
v <- which(d_all_wide$Q76_u18_school > d_all_wide$Q75_u18_school)
d_all_wide$Q75_u18_school[v] <- d_all_wide$Q76_u18_school[v]

v <- which(d_all_wide$Q76_1864_school > d_all_wide$Q75_1864_school)
d_all_wide$Q75_1864_school[v] <- d_all_wide$Q76_1864_school[v]

v <- which(d_all_wide$Q76_o64_school > d_all_wide$Q75_o64_school)
d_all_wide$Q75_o64_school[v] <- d_all_wide$Q76_o64_school[v]

d_all_wide$Q75_school_sum <- rowSums(d_all_wide[, c("Q75_u18_school",
                                                    "Q75_1864_school",
                                                    "Q75_o64_school")],
                                     na.rm = TRUE)

## truncate at "truncate" before adding to school contacts
d_all_wide$Q75_school_sum[d_all_wide$Q75_school_sum>truncate] <- truncate

## add the Q school contacts to the other school contacts
d_all_wide$school_contact_n_Q75 <- d_all_wide$school_contact_n + d_all_wide$Q75_school_sum





# Anderswo -> add to not_specified_contact_n
v <- which(d_all_wide$Q76_u18_else > d_all_wide$Q75_u18_else)
d_all_wide$Q75_u18_else[v] <- d_all_wide$Q76_u18_else[v]

v <- which(d_all_wide$Q76_1864_else > d_all_wide$Q75_1864_else)
d_all_wide$Q75_1864_else[v] <- d_all_wide$Q76_1864_else[v]

v <- which(d_all_wide$Q76_o64_else > d_all_wide$Q75_o64_else)
d_all_wide$Q75_o64_else[v] <- d_all_wide$Q76_o64_else[v]

d_all_wide$Q75_else_sum <- rowSums(d_all_wide[, c("Q75_u18_else",
                                                  "Q75_1864_else",
                                                  "Q75_o64_else")],
                                   na.rm = TRUE)

##add the Q75 work contacts from the below 15 year olds

d_all_wide$dummy_Q75_work_youngage<- 0

d_all_wide$dummy_Q75_work_youngage[d_all_wide$age_group=="Under 1" |
                                     d_all_wide$age_group=="1-4" |
                                     d_all_wide$age_group=="5-9" |
                                     d_all_wide$age_group=="10-14"] <-
d_all_wide$Q75_work_sum[d_all_wide$age_group=="Under 1" |
                            d_all_wide$age_group=="1-4" |
                            d_all_wide$age_group=="5-9" |
                            d_all_wide$age_group=="10-14"]

d_all_wide$Q75_else_sum <-d_all_wide$Q75_else_sum + d_all_wide$dummy_Q75_work_youngage


## truncate at "truncate" before adding to not specified contacts
d_all_wide$Q75_else_sum[d_all_wide$Q75_else_sum>truncate] <- truncate

#add the Q "else" contacts to the not specified contacts
d_all_wide$not_specified_contact_n_Q75 <- d_all_wide$not_specified_contact_n + d_all_wide$Q75_else_sum


```

##add Q75/76 to non-hh

```{r Add Q75 / Q76 contacts to non-hh contacts}

# also add to all non_hh_
d_all_wide$non_hh_contact_n_Q75 <- d_all_wide$non_hh_contact_n + 
  d_all_wide$Q75_work_sum + 
  d_all_wide$Q75_school_sum + 
  d_all_wide$Q75_else_sum


# also add to all_
d_all_wide$all_contact_n_Q75 <- d_all_wide$all_contact_n + 
  d_all_wide$Q75_work_sum + 
  d_all_wide$Q75_school_sum + 
  d_all_wide$Q75_else_sum

```

##add Q75/76 to non-hh truncated overall at 50 (lshtm)

```{r Add Q75 / Q76 contacts to non-hh contacts truncated overall at 50, i.e. like lshtm does it not based on categories}

d_all_wide$Q75_combined <- d_all_wide$Q75_work_sum + d_all_wide$Q75_school_sum + d_all_wide$Q75_else_sum
d_all_wide$Q75_combined[d_all_wide$Q75_combined>truncate_lshtm] <- truncate_lshtm



# also add to all non_hh_
d_all_wide$non_hh_contact_n_Q75_lshtm_ <- d_all_wide$non_hh_contact_n + 
  d_all_wide$Q75_combined

# also add to all_
d_all_wide$all_contact_n_Q75_lshtm <- d_all_wide$all_contact_n + 
  d_all_wide$Q75_combined


```

##data checks and labelling

```{r Some data checks and labelling}

d_all_wide$wave <- as.factor(d_all_wide$wave)
levels(d_all_wide$wave) <- WAVES[as.integer(levels(d_all_wide$wave))]

summary(d_all_wide$age_0)
# age_0 is never below 18 because it is only known for the respondent
# if age is needed, then use age_group!

d_all_wide <- subset(d_all_wide, !is.na(new_id))

# sum of place_ contacts (incl. oth_contact_n) must not be greater than non_hh_contact_n
# CAVE: multiple sites
d_all_wide$sum_place_contact_n <- rowSums(d_all_wide[, c(CONTACT_N,
                                                       "not_specified_contact_n")])
table(d_all_wide$non_hh_contact_n - d_all_wide$sum_place_contact_n,# no negative value 
      d_all_wide$multiple_contact_n,
      useNA = "ifany")



```

## Number of participants per wave
All participants  included regardless of number of waves contributed

```{r descriptive_table}

min_number_waves=1
df <- get_contacts(d_all_wide,min.waves=min_number_waves)

my.render.cat <- function(x) {
  c("", sapply(stats.default(x), function(y) with(y,
                                                  sprintf("%d (%0.0f%%)", FREQ, PCTnoNA))))
}

#table1::table1(~ weekend_weekday + sex2 + age_group_2 + hh_p_incl_0_2| wave, data=df,  render.categorical=my.render.cat,overall=F)

df_unweighted <- df

number_part <- df_unweighted %>% group_by(wave) %>% dplyr::summarise(wave_n=n())
df_unweighted$wave_num <- as.numeric(df_unweighted$wave)

number_of_participants <- ggplot(df_unweighted, aes(x=wave_num))+
      geom_histogram(binwidth=1, fill="grey", colour="black")+
  ggtitle(" Number of participants in each wave in NRW")+
theme(panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),  axis.line = element_line(colour = "black"), plot.title = element_text(face="bold", size=16, colour = "black"), axis.title = element_text(size=16, face="bold", colour = "black"), axis.text.x = element_text(size = 15, colour = "black", angle = 90, vjust=0.5),  axis.text.y = element_text(size = 15, colour = "black")) + 
  scale_x_continuous(breaks = seq(1, current_wave, 2))
number_of_participants

#Warning: Removed 535 rows containing non-finite values (stat_bin)

#auto save
participants <- paste0(path_figures, "/number_of_participants", ".png")
ggsave(participants, width=10, height=7)


```


## Repeated participants

```{r,results="asis"}

df_dummy <- df %>% group_by(new_id) %>% dplyr::summarise(wave_n=n()) ## add dplyr::, no longer error
df_dummy$num_wave_included<-min_number_waves
df_dummy$wave_n_factor <- as.factor(df_dummy$wave_n)
df_dummy$wave_n_cat <- as.factor(ifelse(df_dummy$wave_n < 2, '1',
                     ifelse(df_dummy$wave_n < 5, '2-4', 
                     ifelse(df_dummy$wave_n < 10, '5-9', 
                     ifelse(df_dummy$wave_n < 15, '10-14', 
                     ifelse(df_dummy$wave_n < 20, '15-19', 
                     ifelse(df_dummy$wave_n < 25, '20-24', 
                            '>=25')))))))
df_dummy$wave_n_cat <- factor(df_dummy$wave_n_cat, levels=c("1", "2-4", "5-9", "10-14", "15-19", "20-24",">=25"))

# lable table
# table1::lable(df_dummy$num_wave_included) <- "wanted name"
table1::table1(~num_wave_included + wave_n + wave_n_factor + wave_n_cat, data=df_dummy)

```

## Mean all contacts
```{r ,results="asis"}

#mean contact
table1::table1(~all_contact_n_Q75 + all_contact_n | wave, data=df)

```

# Distribution figures

## Age group
```{r}

#Age Group
df_unweighted_histo <- df_unweighted %>% select(new_id, wave, age_group_2, wave_num)
df_unweighted_histo <- df_unweighted_histo %>% group_by(wave_num, age_group_2) %>% dplyr::summarise(age_group_2_n=n())

age_per_wave <- ggplot(df_unweighted_histo, 
               aes_string(x = "wave_num", y = "age_group_2_n", fill = "age_group_2")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
    labs(fill=" Age in years",x= "Wave",y = "Percentage") + # rename legend title
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))
age_per_wave
age_groups_part <- paste0(path_figures, "/age_groups_part", ".png")
ggsave(age_groups_part, width=10, height=7)


```

## Sex
```{r}
#Sex
df_unweighted_histo <- df_unweighted %>% select(new_id, wave, sex2, wave_num)
df_unweighted_histo <- df_unweighted_histo %>% group_by(wave_num, sex2) %>% dplyr::summarise(sex2_n=n())

sex_per_wave <- ggplot(df_unweighted_histo, 
               aes_string(x = "wave_num", y = "sex2_n", fill = "sex2")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
  labs(fill=" Gender",x= "Wave",y = "Percentage") + # rename legend title
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))
sex_per_wave
sex_part <- paste0(path_figures, "/sex_part", ".png")
ggsave(sex_part, width=10, height=7)



```

## hh size
```{r}

#HH Size
df_unweighted_histo <- df_unweighted %>% select(new_id, wave, hh_p_incl_0_3, wave_num)
df_unweighted_histo <- df_unweighted_histo %>% group_by(wave_num, hh_p_incl_0_3) %>% dplyr::summarise(hh_p_incl_0_3_n=n())

hh_per_wave <- ggplot(df_unweighted_histo, 
               aes_string(x = "wave_num", y = "hh_p_incl_0_3_n", fill = "hh_p_incl_0_3")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
   labs(fill=" Household size",x= "Wave",y = "Percentage") + # rename legend title
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))
hh_per_wave
hh_part <- paste0(path_figures, "/hh_part", ".png")
ggsave(hh_part, width=10, height=7)
```


## Mask wearing

```{r}
table1(~mask_0 + transportno_0|wave, data=df)

#Mask 

df_histo <- df %>% select(new_id, wave, mask_0)
df_histo$wave_num <- as.numeric(df_histo$wave)
df_histo <- df_histo %>% group_by(wave_num, mask_0) %>% dplyr::summarise(mask_0_n=n())


                      
mask_per_wave <- ggplot(df_histo, 
               aes_string(x = "wave_num", y = "mask_0_n", fill = "mask_0")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
    scale_fill_manual(values = c("#663399", "#028482"),
                      name = "Mask use",
                      labels = c("No", "Yes")) + 
    xlab("Wave") +
    ylab("Percentage") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

mask_per_wave
mask_per_wave_all <- paste0(path_figures, "/mask_all", ".png")
ggsave(mask_per_wave_all, width=10, height=7)




#Mask restricted to those with at least one non-hh contact 
df_histo <- df %>% filter(non_hh_contact_n_Q75>0) %>% select(new_id, wave, mask_0)
df_histo$wave_num <- as.numeric(df_histo$wave)
df_histo <- df_histo %>% group_by(wave_num, mask_0) %>% dplyr::summarise(mask_0_n=n())

mask_per_wave_restricted <- ggplot(df_histo, 
               aes_string(x = "wave_num", y = "mask_0_n", fill = "mask_0")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
    scale_fill_manual(values = c("#663399", "#028482"),
                      name = "Mask use",
                      labels = c("No", "Yes")) + 
    xlab("Wave") +
    ylab("Percentage") +
    ggtitle("Mask restricted to those with at least one non-hh contact")+
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 4, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

mask_per_wave_restricted
mask_per_wave_restricted <- paste0(path_figures, "/mask_restricted", ".png")
ggsave(mask_per_wave_restricted, width=10, height=7)

```

## Transport Use

```{r}

#Transport
##remember No means yes, used public transport
table1(~ transportno_0|wave, data=df)

df_histo <- df %>% select(new_id, wave, transportno_0)
df_histo$wave_num <- as.numeric(df_histo$wave)
df_histo <- df_histo %>% group_by(wave_num, transportno_0) %>% dplyr::summarise(transportno_0_n=n())


                      
transport_all <- ggplot(df_histo, 
               aes_string(x = "wave_num", y = "transportno_0_n", fill = "transportno_0")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
    scale_fill_manual(values = c("#990033", "#336699"),
                      name = "Transport use",
                      labels = c("Yes", "No")) + 
    xlab("Wave") +
    ylab("Percentage") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

transport_all
transport_per_wave_all <- paste0(path_figures, "/transport_all", ".png")
ggsave(transport_per_wave_all, width=10, height=7)
```

## Percent people having non-hh contact
```{r}


df_histo <- df %>% select(new_id, wave, non_hh_contact_n_Q75)
df_histo$wave_num <- as.numeric(df_histo$wave)
df_histo$non_hh_contacts_over_0[df_histo$non_hh_contact_n_Q75==0] <- "No"
df_histo$non_hh_contacts_over_0[df_histo$non_hh_contact_n_Q75>0] <- "Yes"
table1(~ non_hh_contacts_over_0 + as.factor(non_hh_contact_n_Q75)|wave, data=df_histo)
df_histo <- df_histo %>% group_by(wave_num, non_hh_contacts_over_0) %>% dplyr::summarise(non_hh_contacts_over_0_n=n())


no_non_hh_contact <- ggplot(df_histo, 
               aes_string(x = "wave_num", y = "non_hh_contacts_over_0_n", fill = "non_hh_contacts_over_0")) + 
    geom_bar(position = "fill", stat = "identity") +
    scale_y_continuous(labels = scales::percent_format(),expand = c(0,0)) +
    scale_x_continuous(breaks = seq(1, current_wave, 1))+
    scale_fill_manual(values = c("#663399", "#028482"),
                      name = "Non household\ncontacts",
                      labels = c("No", "Yes")) + 
    xlab("Wave") +
    ylab("Percentage") +
    theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          plot.background = element_blank(),
          plot.title = element_text(colour = "black", size = base_size + 2, face = "bold",
                                    hjust = 0.5),
          strip.background = element_blank(),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

no_non_hh_contact
no_non_hh_contact_name <- paste0(path_figures, "/no_non_hh_contact", ".png")
ggsave(no_non_hh_contact_name, width=10, height=7)



```

# Mean contacts over time

```{r}

#method1:
# plot mean contact
ggplot(d_all_wide, aes(x=wave_0, y=all_contact_n_Q75))+ 
    stat_summary(geom="ribbon", fun.data=mean_cl_normal, 
                 fun.args=list(conf.int=0.95), fill="lightblue")+
    stat_summary(geom="line", fun=mean, linetype="dashed")+
    stat_summary(geom="point", fun=mean, color="red")+
  scale_x_continuous(breaks = seq(1,current_wave,2))+
  coord_cartesian( ylim = c(0, 6))+
  # scale_x_discrete("",labels = c(WAVES))+ #
  labs(y="Mean_all_contact_n_Q75",x="wave")+
  ggtitle("All contact")+
   # theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = base_size + 4, face = "bold",
                                    hjust = 0),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

# plot mean contact_hh
ggplot(d_all_wide, aes(x=wave_0, y=hh_contact_n))+ 
    stat_summary(geom="ribbon", fun.data=mean_cl_normal, 
                 fun.args=list(conf.int=0.95), fill="lightblue")+
    stat_summary(geom="line", fun=mean, linetype="dashed")+
    stat_summary(geom="point", fun=mean, color="red")+
  scale_x_continuous(breaks = seq(1,current_wave,2))+
   coord_cartesian( ylim = c(0, 6))+
  labs(y="Mean_contact_hh",x="Wave")+
  ggtitle("Household contact")+
   # theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = base_size + 4, face = "bold",
                                    hjust = 0),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))
# plot mean contact_non_hh
ggplot(d_all_wide, aes(x=wave_0, y=non_hh_contact_n_Q75))+ 
    stat_summary(geom="ribbon", fun.data=mean_cl_normal, 
                 fun.args=list(conf.int=0.95), fill="lightblue")+
    stat_summary(geom="line", fun=mean, linetype="dashed")+
    stat_summary(geom="point", fun=mean, color="red")+
  scale_x_continuous(breaks = seq(1,current_wave,2))+
   coord_cartesian( ylim = c(0, 6))+
  labs(y="Mean_contact_non_hh_Q75", x="Wave")+
  ggtitle("Non-household contact")+
   # theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          plot.title = element_text(colour = "black", size = base_size + 4, face = "bold",
                                    hjust = 0),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))

# all contact in one plot
dt <- d_all_wide %>% select("wave_0","all_contact_n_Q75","non_hh_contact_n_Q75","hh_contact_n")
dt <- melt(dt,id.vars="wave_0")

ggplot(dt, aes( x=wave_0, y=value, colour=variable, fill=variable ))+ 
    stat_summary(geom="ribbon", fun.data=mean_cl_normal, 
                 fun.args=list(conf.int=0.95))+
    stat_summary(geom="line", fun=mean, linetype="dashed")+
    stat_summary(geom="point", fun=mean)+
  # scale_fill_manual(values = c("#fee8c8","#e7e1ef"))+
  scale_fill_manual(values = c("#fee8c8","#e7e1ef","#2b8cbe"))+
  
  scale_x_continuous(breaks = seq(1,current_wave,2))+
  # scale_x_discrete("",labels = c(WAVES))+ #
  labs(y="Mean_contacts_Q75",x="wave")+
   ggtitle("Mean contacts over time in NRW")+
   # theme_bw() +
    theme(axis.text.x = element_text(colour = "black", size = 15, 
                                     angle = 90, hjust = 0.5, vjust = 0,5),
          axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
          axis.title = element_text(colour = "black", size = 16, face = "bold"),
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.position = "right",
          legend.text = element_text(colour = "black", size = 15),
          legend.title = element_text(colour = "black", size = 16, face = "bold"),
          
          plot.title = element_text(colour = "black", size = base_size + 4, face = "bold",
                                    hjust = 0.5),
          strip.text = element_text(colour = "black", size = base_size, face = "bold"))
rm(dt)

#https://stackoverflow.com/questions/53180486/plotting-average-of-multiple-groups-across-time-in-ggplot2 (plot different group)

# another approach show similar result

# #method2
# mean.contact = d_all_wide %>%
#   group_by(wave_0) %>%
#   dplyr::summarise(N = n(),
#             avg.contact = mean(all_contact_n_Q75),
#             SE.low = avg.contact - (sd(all_contact_n_Q75)/sqrt(N)),
#             SE.high = avg.contact + (sd(all_contact_n_Q75)/sqrt(N)))
# 
# 
# plot(avg.contact ~ wave_0, data = mean.contact,ylim=c(0,6), type = 'n')
# polygon(c(mean.contact$wave_0, rev(mean.contact$wave_0)),
#         c(mean.contact$SE.low,rev(mean.contact$SE.high)), density = 200, col ='grey90')
# 
# points(avg.contact ~ wave_0, data = mean.contact, pch = 19, col = 'firebrick')


```


