---
title: "Mapping_COVID-19 Incidence vs SES"
author: "Thi Phuong Huynh"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true # able of contents to the left, visible even when the document is scrolled
---

# set up

Date: <b>`r format(Sys.Date(), "%B %d, %Y")`</b>

All computations were performed with `r R.Version()$version.string`.

```{r setup, include=FALSE}

rm(list = ls())
knitr::opts_chunk$set(fig.retina = 1, fig.height = 7, fig.width = 14,
                      echo = FALSE, message = FALSE, warning = FALSE,
                      results='hide')

Sys.setlocale("LC_TIME", "C")
BEGIN_RMD <- Sys.time() # Keeping track of running time
set.seed(75876342)
options(warn = 1) # If warn is one, warnings are printed as they occur.


library(sf) # for reading shape files into R
library(tmap)#for creating the map
library(dplyr)
library(tidyverse)
library(ggpubr) #ggarrange
library(pheatmap)

path_data <- paste0("C:/Users/huynh/sciebo/NRW_descriptive/data")


```


#changeable variable

```{r demographic data}
#pop######################
NRW_pop <- 17925570
NRW_under12 <- 2014762
NRW_vacc <- NRW_pop - NRW_under12
start_day <- as.Date("2020-02-27")# data before this day won't be counted
# pop(https://www.destatis.de/DE/Home/_inhalt.html)
#ref map: https://www.mags.nrw/matchingberater-karte
#NRW pop. by county: http://www.citypopulation.de/en/germany/cities/nordrheinwestfalen/
#NRW pop. by county( original from destatis): https://www-genesis.destatis.de/genesis/online?sequenz=statistikTabellen&selectionname=12411&language=en#abreadcrumb


```

#data input
```{r data input}

#NRW_pop_county#####################
pop <- read.csv(paste0(path_data,"/NRW_cencus/NRW_pop_bycounty_NUTS_ID.csv"),row.names = 1, encoding="UTF-8")
pop <- pop%>% select(c("pop_n", "NUTS_ID")) #county name has error ->rm it

#NUTS_3##############################
nuts3 <- read_sf(paste0(path_data,"/NUTS/NUTS_RG_20M_2021_3035.shp")) #Eurostat
# nuts3 <- read_sf(paste0(path_data,"/NUTS/nuts1000_12-31.gk3.shape/nuts1000_1231_3")) # RKI
nuts3 <- nuts3 %>% filter(CNTR_CODE == "DE") # chose only Germany
nuts3$NAME_LATN <- gsub(",.*", "",nuts3$NAME_LATN) #rm string after comma
colnames(nuts3)[which(names(nuts3) == "NAME_LATN")] <- "county"  # rename a col
nuts3 <- nuts3 %>% filter(nuts3$NUTS_ID %in% pop$NUTS_ID) # choose only NRW
nuts3 <- merge(nuts3,pop, by = "NUTS_ID") # add population

# Deprivation upto 2015
# download.file("https://raw.githubusercontent.com/lekroll/GISD/master/Revisions/2019/Bund/Kreis/Kreis.csv", destfile = paste0(path_data,"/GISD/GISD_upto2015.csv")) # download data from Github## check update version

gisd <- read.csv(paste0(path_data,"/GISD/GISD_upto2015.csv"), sep = ",",row.names = 1)
colnames(gisd) <- c("county_id","county","year","pop","GISD_Score","GISD_5","GISD_10","GISD_k")
gisd <- gisd %>%filter(year == 2015) # the most recent data
# gisd <- gisd%>% filter(substr(county_id,1,2))

gisd$county <- gsub(",.*", "", gisd$county) #rm string after comma
gisd <- merge(nuts3,gisd, by = "county") # add NUTS info
# gisd$GISD_5 <- as.factor(gisd$GISD_5)


#COVID-19###########################
dat = read.csv(paste0(path_data,"/211229_Fall-Liste.csv"), sep=";", encoding="UTF-8",row.names = 1)# encoding="UTF-8" : umlaut character
colnames(dat)
dat <- dat %>% select(-contains("InterneRef")) #rm
names(dat) <- c("rep_date","county", "disease_start", "age",'hospitalized')   #rename
dat$county[dat$county == "StadtRegion Aachen"] <- "SK StadtRegion Aachen" #change to the same format with other counties
dat$county <- gsub("^.{0,3}", "", dat$county)# Replace first 3 characters (SK ) with empty string ""
dat$rep_date<- as.Date(dat$rep_date, "%Y-%m-%d")
dat$disease_start<- as.Date(dat$disease_start, "%Y-%m-%d")
dat$county <- as.factor(dat$county)
dat$rep_week <- as.integer((as.Date(dat$rep_date)-as.Date("2020-01-01"))/7+1) #wednessday starts a week
dat$maxrepweek <- max(dat$rep_week) 
# remove rep week 8 because of insufficient data 
dat <- dat %>% filter(rep_week >=10)#


```

##cleaning data

```{r}
#COVID-19###########################

#revert week to date: 
#check which day is starting of a week : Wednesday
dat$rep_week_date <- lubridate::ymd( "2020-01-01" ) + lubridate::weeks(dat$rep_week-1)
dat$rep_week_date <- as.Date(dat$rep_week_date)
dat$agegroup<- dat$age
dat$agegroup <- cut(dat$agegroup, breaks=c(-Inf, 4, 9,14, 19,24,29,34,39,44,49,54,59,64,69,74,79,84,89, Inf))
dat$agegroup <- factor(dat$agegroup, levels=c("(-Inf,4]", "(4,9]", "(9,14]", "(14,19]", "(19,24]", "(24,29]",
                                              "(29,34]", "(34,39]", "(39,44]", "(44,49]", "(49,54]", 
                                              "(54,59]", "(59,64]", "(64,69]", "(69,74]", "(74,79]", "(79,84]", "(84,89]", 
                                              "(89, Inf]"),
                       labels=c("0-4","5-9","10-14", "15-19", "20-24", "25-29", "30-34", "35-39",
                                "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74",
                                "75-79", "80-84", "85-89", ">90"), ordered=T)
# These two counties:  "Mülheim an der Ruhr", "Städteregion Aachen" (nuts3) is different from dat ("Mülheim a.d.Ruhr", "StadtRegion Aachen" )
##rename it to be inline with other dataset

dat$county <- gsub("Mülheim a.d.Ruhr", "Mülheim an der Ruhr", dat$county)
dat$county <- gsub("StadtRegion Aachen", "Städteregion Aachen", dat$county)


#group data by county and wave
dat_county <- dat %>% group_by(county) %>%
  dplyr::summarise(cases=n())%>%
  ungroup() 
dat_county_wave1 <- dat %>%filter(rep_date <= as.Date("2020-06-30")) %>% group_by(county) %>%
  dplyr::summarise(cases_wave1=n())%>%
  ungroup() 
dat_county_wave2 <- dat %>%filter(rep_date > as.Date("2020-06-30")&rep_date <= as.Date("2021-02-22")) %>% group_by(county) %>%
  dplyr::summarise(cases_wave2=n())%>%
  ungroup() 
dat_county_wave3 <- dat %>%filter(rep_date > as.Date("2021-02-22")&rep_date <= as.Date("2021-07-12")) %>% group_by(county) %>%
  dplyr::summarise(cases_wave3=n())%>%
  ungroup() 
dat_county_wave4 <- dat %>%filter(rep_date > as.Date("2021-07-12")&rep_date <= as.Date("2021-12-30")) %>% group_by(county) %>%
  dplyr::summarise(cases_wave4=n())%>%
  ungroup() 

# dat_county1 <- left_join (dat_county,dat_county_wave1,dat_county_wave2,dat_county_wave3,dat_county_wave4, by="county")
dat_county <- left_join (dat_county,dat_county_wave1)
dat_county <- left_join (dat_county,dat_county_wave2)
dat_county <- left_join (dat_county,dat_county_wave3)
dat_county <- left_join (dat_county,dat_county_wave4)
rm(dat_county_wave1,dat_county_wave2,dat_county_wave3,dat_county_wave4)

# write.csv(dat_county,"C:/Users/huynh/sciebo/NRW_descriptive/data/case_county_waves.csv",
#           fileEncoding = "UTF-8")# export and then mannualy combined with NUTS_3 data


# dat_county <- read.csv(paste0(path_data,"/case_county_waves_NUTS_ID.csv"), encoding="UTF-8")

dat_county <- merge(dat_county,nuts3, by = "county")

# dat_county <- merge(dat_county , pop, by = c("NUTS_ID"), all = T) #
# nuts3 <- merge(nuts3,dat_county, by = "NUTS_ID")



```

# SES

* NRW social economic status
ref: https://github.com/lekroll/GISD

In order to be able to map regional differences in socioeconomic status, the German Index of Social Deprivation is used (Kroll et al. 2018, p. 105).
The index is composed of the three equally weighted dimensions of education, occupation and income.
The data underlying the dimensions are provided by the Indicators and Maps of Spatial and Urban Development (INKAR) database of the Federal Institute for Research on Building, Urban Affairs and Spatial Development (Bundesinstitut für Bau-, Stadt- und Raumforschung 2020 /

https://www.bbsr.bund.de/BBSR/EN/home/_node.html;jsessionid=5D48C9E3CCEE2DF7D9A30B3C58D7986E.live21324).
Indicators were selected which were available as time series from 1998 to 2012 (in the current version of the index used here, until 2014). If this was not the case, the missing values of the respective variables were imputed using regression analyses.

```{r}

#GISD5
legend_label=c("1", "2", "3","4","5")

panel_gisd5 <- tm_shape(gisd) +
  tm_fill("GISD_5", palette = "Blues", legend.show = F) + #
  tm_borders("black") +
  tm_add_legend(title = "Deprivation index", labels = legend_label, col = RColorBrewer::brewer.pal(5, "Blues")) +
  # \n : line down
  tm_layout(title = "Social econmic status", title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0.1,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")
panel_gisd5 

# #GISD_10
# legend_label=c("1", "2", "3","4","5","6", "7", "8","9","10")
# gisd10 <- tm_shape(gisd) +
#   tm_fill("GISD_10", palette = "Blues", legend.show = F) + #
#   tm_borders("black") +
#   tm_add_legend(title = "GISD_10",labels = legend_label, col = RColorBrewer::brewer.pal(10, "Blues")) +
#   # \n : line down
#   tm_layout(title = "SES", title.fontfamily = "sans", title.size = 1.5,
#             title.fontface= "bold", title.position= c(0.15,0.95),frame=F,
#             legend.outside = F, legend.frame = F,
#             legend.position = c(0.9,0.0), legend.width = 1,
#             legend.title.size = 1.5, legend.text.size= 1.2,
#             legend.title.fontfamily ="sans",legend.title.fontface ="bold")
# 
# 
# # multiple plots in the same page 
# ggpubr:: ggarrange(tmap_grob(gisd5), # tmap_grob: convert tmap into grob
#                    tmap_grob(gisd10),
#                    # labels = c("A", "B"),
#                    ncol = 1, nrow = 2)
# 
# # # Plotting a grid of plots
# # cowplot::plot_grid(w1,w2,
# #  ncol = 1, nrow = 2)


```


# COVID-19 mapping
##Wave1

At the start, the incidences are still small. The incidence grouping should also be small to see the difference among counties. So the colour visualization is to compare within the wave. However, from wave two onward, the scale is similar.  

For across waves comparison, please notice the legend!

Testing volumes may have been insufficient early in the pandemic 

```{r}
title <-"COVID-19 reported_W1\n 27.02-30.06.2020"
# title <-"COVID-19 reported_W2\n 01.07-22.02.2021"
# title <-"COVID-19 reported_W3\n 23.02-12.07.2021"
# title <-"COVID-19 reported_W4\n 13.07-30.12.2021"
# titlel<-"COVID-19 reported\n 27.02.20-30.12.21"



nuts3_case <- dat_county %>%select("NUTS_ID", "cases_wave1","pop_n")%>%
  mutate(incper10k = cases_wave1/pop_n*10000)%>%
  mutate(incper10k_group = cut(incper10k, breaks=c(-Inf,10,15,20,25,30,35,40,45,Inf)))

nuts3_case <-merge(nuts3, nuts3_case , by = "NUTS_ID")

#copy abow where appropriate
legend_label=c("0-10",">10-15",">15-20", ">20-25", ">25-30", ">30-35", ">35-40", ">40-45",">45")

w1 <- tm_shape(nuts3_case) +
  tm_fill("incper10k_group", palette = "Purples", legend.show = F) + #Blues
  tm_borders("black") +
  tm_add_legend(title = "Incidence \n (per 10k)", labels = legend_label, col = RColorBrewer::brewer.pal(9, "Purples")) +
  # \n : line down
  tm_layout(title = paste0(title), title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")

# w1

```

##Wave 2

```{r}

# title <-"COVID-19 reported_W1\n 27.02-30.06.2020"
title <-"COVID-19 reported_W2\n 01.07-22.02.2021"
# title <-"COVID-19 reported_W3\n 23.02-12.07.2021"
# title <-"COVID-19 reported_W4\n 13.07-30.12.2021"
# titlel<-"COVID-19 reported\n 27.02.20-30.12.21"




nuts3_case <- dat_county %>%select("NUTS_ID", "cases_wave2","pop_n")%>%
  mutate(incper10k = cases_wave2/pop_n*10000)%>%
  mutate(incper10k_group = cut(incper10k, breaks=c(-Inf,150,175,200,225,250,275,300,350,Inf)))

nuts3_case <-merge(nuts3, nuts3_case , by = "NUTS_ID")

#label
legend_label=c("0-150", ">150-175", ">175-200",">200-225", ">225-250", ">250-275", ">275-300", ">300-350", ">350")

w2 <- tm_shape(nuts3_case) +
  tm_fill("incper10k_group", palette = "Blues", legend.show = F) + #Blues
  tm_borders("black") +
  tm_add_legend(title = "Incidence \n (per 10k)", labels = legend_label, col = RColorBrewer::brewer.pal(9, "Blues")) +
  # \n : line down
  tm_layout(title = paste0(title), title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")
# w2



```

##Wave 3 

```{r}
# title <-"COVID-19 reported_W1\n 27.02-30.06.2020"
# title <-"COVID-19 reported_W2\n 01.07-22.02.2021"
title <-"COVID-19 reported_W3\n 23.02-12.07.2021"
# title <-"COVID-19 reported_W4\n 13.07-30.12.2021"
# titlel<-"COVID-19 reported\n 27.02.20-30.12.21"



nuts3_case <- dat_county %>%select("NUTS_ID", "cases_wave3","pop_n")%>%
  mutate(incper10k = cases_wave3/pop_n*10000)%>%
  mutate(incper10k_group = cut(incper10k, breaks=c(-Inf,150,175,200,225,250,275,300,350,Inf)))

nuts3_case <-merge(nuts3, nuts3_case , by = "NUTS_ID")

#label
legend_label=c("0-150", ">150-175", ">175-200",">200-225", ">225-250", ">250-275", ">275-300", ">300-350", ">350")

w3 <- tm_shape(nuts3_case) +
  tm_fill("incper10k_group", palette = "Blues", legend.show = F) + #Blues
  tm_borders("black") +
  tm_add_legend(title = "Incidence \n (per 10k)", labels = legend_label, col = RColorBrewer::brewer.pal(9, "Blues")) +
  # \n : line down
  tm_layout(title = paste0(title), title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")
# w3

```

##Wave 4 

```{r}
# title <-"COVID-19 reported_W1\n 27.02-30.06.2020"
# title <-"COVID-19 reported_W2\n 01.07-22.02.2021"
# title <-"COVID-19 reported_W3\n 23.02-12.07.2021"
title <-"COVID-19 reported_W4\n 13.07-29.12.2021"
# titlel<-"COVID-19 reported\n 27.02.20-30.12.21"

wave <- dat_county %>% select("NUTS_ID", "cases_wave4","pop_n")
wave$incper10000<- wave$cases_wave4/wave$pop_n*10000





nuts3_case <- dat_county %>%select("NUTS_ID", "cases_wave4","pop_n")%>%
  mutate(incper10k = cases_wave4/pop_n*10000)%>%
  mutate(incper10k_group = cut(incper10k, breaks=c(-Inf,150,175,200,225,250,275,300,350,Inf)))

nuts3_case <-merge(nuts3, nuts3_case , by = "NUTS_ID")

#label
legend_label=c("0-150", ">150-175", ">175-200",">200-225", ">225-250", ">250-275", ">275-300", ">300-350", ">350")

w4 <- tm_shape(nuts3_case) +
  tm_fill("incper10k_group", palette = "Blues", legend.show = F) + #Blues
  tm_borders("black") +
  tm_add_legend(title = "Incidence \n (per 10k)", labels = legend_label, col = RColorBrewer::brewer.pal(9, "Blues")) +
  # \n : line down
  tm_layout(title = paste0(title), title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")
# w4

```

## entire pandamic and 4 waves

Criteria for defining a wave?

```{r}
# title <-"COVID-19 reported_W1\n 27.02-30.06.2020"
# title <-"COVID-19 reported_W2\n 01.07-22.02.2021"
# title <-"COVID-19 reported_W3\n 23.02-12.07.2021"
# title <-"COVID-19 reported_W4\n 13.07-30.12.2021"
title <-"COVID-19 reported_4waves\n 27.02.20-29.12.21"


nuts3_case <- dat_county %>%select("NUTS_ID", "cases","pop_n")%>%
  mutate(incper10k = cases/pop_n*10000)%>%
  mutate(incper10k_group = cut(incper10k, breaks=c(-Inf,550,600,650,700,750,800,850,900,Inf)))

nuts3_case <-merge(nuts3, nuts3_case , by = "NUTS_ID")

#label
legend_label=c(">450-550", ">550-600",">600-650", ">650-700",">700-750", ">750-800", ">800-850", ">850-900",">900")

w_all <- tm_shape(nuts3_case) +
  tm_fill("incper10k_group", palette = "Oranges", legend.show = F) + #Blues
  tm_borders("black") +
  tm_add_legend(title = "Incidence \n (per 10k)", labels = legend_label, col = RColorBrewer::brewer.pal(9, "Oranges")) +
  # \n : line down
  tm_layout(title = paste0(title), title.fontfamily = "sans", title.size = 1.5,
            title.fontface= "bold", title.position= c(0,0.9),frame=F,
            legend.outside = F, legend.frame = F,
            legend.position = c(0.85,0.0), legend.width = 1,
            legend.title.size = 1.5, legend.text.size= 1.2,
            legend.title.fontfamily ="sans",legend.title.fontface ="bold")
# w_all



# multiple plots in the same page 
current.mode <- tmap_mode("plot")
tmap_arrange(panel_gisd5,w_all, widths = c(0.5, 0.5))
tmap_mode(current.mode)


```


```{r}

# # multiple plots in the same page 
# ggpubr:: ggarrange(tmap_grob(w1), # tmap_grob: convert tmap into grob
#                    tmap_grob(w2),
#                    tmap_grob(w3),
#                    tmap_grob(w4),
#                    # labels = c("A", "B"),
#                    ncol = 2, nrow = 2)

current.mode <- tmap_mode("plot")
tmap_arrange(w1, w2, w3, w4, widths = c(0.5, 0.5))
tmap_mode(current.mode)


```


# Heat map: 


## Group scale 

```{r}

# data at week level 
dat_week <- dat %>%group_by(rep_week_date,county)%>% summarise(case =  n())
dat_week <- merge(dat_week, gisd %>%select(county,pop_n, GISD_5), by = "county")
dat_week$case_per100k<- dat_week$case/dat_week$pop_n*100000

#division 0
# dat_week$case_per100k_grouped <- cut(dat_week$case_per100k, breaks=c(-Inf, 5, 10, 15, 20,25,100,200,300,400,Inf))
dat_week$case_per100k_grouped <- cut(dat_week$case_per100k, breaks=c(-Inf, 25, 50, 75, 100,150,200,250,300,350,400,Inf))




# #label
legend_label=c("0-25", ">25-50", ">50-75",">75-100", ">100-150", ">150-200",">200-250", ">250-300",">300-350", ">350-400", ">400")

dat_week %>%
  ggplot(aes(rep_week_date,county)) +
  geom_tile(aes(fill=case_per100k_grouped ), colour = "black")+
  geom_text(aes(label = round(case_per100k )), size = 1, colour = "#585858") + #size of number in each cell
  #division 0
  scale_fill_manual(values=c("#FFF7FC","#EDE7F3", "#D0D1E6", "#A6BDDC", "#74AAD0",
                             "#3691C0", "#0470B0", "#044E7B", "#333F50", "#404040", "#262626"),
                    label = legend_label) +
  ## division 1,2,3
  # scale_fill_brewer(palette = "Blues")+ #BuPu, BuGn, Blues, Oranges,Reds,....
  labs(fill = "incidence \n(per 100k)", x="", y="")+
  ggtitle("NRW_ weekly COVID-19 Incidence per 100k ")+
  # facet_wrap(~GISD_5)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.position="right",
        legend.title=element_text(size=18, colour = "black", face = "bold") ,
        legend.text=element_text(size=17, colour = "black"),
        axis.title = element_text(size=18, face="bold", colour = "black"),
        plot.title = element_text(face="bold", size=18, hjust=0.5),
        axis.text.x = element_text(size = 8,  hjust = 1, colour = "black", angle = 30, face = "bold"),
        axis.text.y = element_text(size = 8, face = "bold")) + 
  scale_x_date(date_labels="%Y-%m-%m", date_breaks = "30 days", expand = c(0, 0)) +
  # scale_x_continuous(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0))



```

## Continuous scale

```{r}


# continues scale
ggplot(dat_week, aes(rep_week_date, county)) +
  geom_tile(aes(fill = case_per100k)) +
  # coord_equal() +
  # ggtitle(paste0("Wave ", wave_n)) +
  # geom_text(aes(label=sprintf("%0.1f", round(case_per100k, digits = 2))), size = 2) +
  scale_fill_gradient2(low = "white",
                       # mid = "white",
                       high = "blue", limits = c(0,600), midpoint = 12) +
  guides(fill = guide_colourbar(barwidth = 0.5,
                                 barheight = 5, title = "Incidence \n(per100k)")) +
 scale_x_date(date_labels="%Y-%m-%m", date_breaks = "30 days", expand = c(0, 0))+
  # scale_x_date(breaks = unique(dat_week$rep_week_date))+ # display all dates on x axis
   ggtitle("NRW_ weekly COVID-19 Incidence per 100k ")+
  theme(legend.position = "right")+
  theme(plot.title = element_text(size = 10, face = "bold",hjust = 0.5),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 6, face = "bold",angle = 30, vjust = 0.5),
        axis.text.y = element_text(size = 8, face = "bold"),
        axis.ticks.x = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"), # reduce space for combination plot later

                panel.background = element_blank())


```

## Add SES annotation

COVID-19 incidence in each county over time vs social economic status

**This figure can be sum by 4 wave only**


```{r}

# Heat map with deprivation index (GISD) annotation
dat_week_long <- dat_week %>% select(GISD_5,county,rep_week_date,case_per100k)
dat_week_long <- dat_week_long[order(dat_week_long$rep_week_date),] # sort data by time report

dat_week_long <- dat_week_long %>%
  pivot_wider(names_from = rep_week_date, values_from = case_per100k)#Transposing row values to colum
dat_week_long <- dat_week_long[order(dat_week_long$GISD_5),] # sort data by GISD

#annotation set
label_gisd <- dat_week_long %>% select(county,GISD_5)# prepare for anotation heatmap
rownames(label_gisd ) <- label_gisd$county
label_gisd <- as.data.frame(label_gisd)
label_gisd$GISD_5 <- as.character(label_gisd$GISD_5)
label_gisd <- label_gisd[,-1, drop=F] # avoid row name disappear
colnames(label_gisd) <- c("Deprivation_index")

dat_week_long <- dat_week_long[,-1]# rm GISD
rownames(dat_week_long) <- dat_week_long$county # convert county into rownames
dat_week_long <- as.data.frame((dat_week_long )) # matrix for heatmap
dat_week_long <- dat_week_long [,-1, drop=F]  # avoid row name disappear

annotation_colors = list(
 Deprivation_index = c("1"="#54278f","2"="#756bb1","3"="#9e9ac8","4"="#cbc9e2","5"="#f2f0f7"))

pheatmap(dat_week_long,cluster_rows = F, cluster_cols = F,RColorBrewer::brewer.pal(name = "Blues", n =9), annotation_row = label_gisd,
         annotation_colors= annotation_colors,annotation_names_row=F,
           fontsize = 10,fontsize_row =7,fontsize_col = 6, legend_breaks = c(100, 200, 300, 400,500),
         main = "NRW_ weekly COVID-19 Incidence per 100k ", legend_labels = c("100", "200", "300", "400","500"), legend = T,)



# ggsave(paste0(path_results,"  ",".png"),com_FIG_1, width=13, height=8)


```

