---
title: "Vaccination against SARS-CoV-2 in NRW"
author: "Thi Phuong Huynh"
date: "2/7/2022"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true # able of contents to the left, visible even when the document is scrolled
---

# set up

Date: <b>`r format(Sys.Date(), "%B %d, %Y")`</b>

All computations were performed with `r R.Version()$version.string`.


```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(fig.retina = 1, fig.height = 7, fig.width = 14,
                      echo = FALSE, message = FALSE, warning = FALSE,
                      results='hide')
# Loading packages
library(epiDisplay)
library("deSolve")
library(plyr)
library(ggplot2)
library("RColorBrewer")
library(wesanderson)
library("ggsci")
library(scales)
library(openxlsx)
library("readr")
library(dplyr)
library(ggrepel)
library(directlabels)
library(writexl)
library(cowplot)
library(Cairo)
library("readxl")
library(zoo)
library(grid)
library(epiDisplay)
library(ggpubr)
library(glue)
library(stringr)
library(tidyr)
library(gridExtra)

set.seed(123456789)


path_data<- paste0("C:/Users/huynh/sciebo/NRW_descriptive/data/")
path_data_code <- paste0("C:/Users/huynh/sciebo/NRW_descriptive/gitHub/NRW_COVID-19_decriptive/codes/data_codes")
######################

#http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html
# Stacked bar plot

```

#Changaeble variables

```{r}

Date_today <- as.Date('29.12.2021', format='%d.%m.%Y') 
#pop
NRW_pop <- 17925570
NRW_under12 <- 2014762
NRW_pop_vacc <- NRW_pop - NRW_under12


```


#Data

BUND data is summed by vaccine types daily while LK data is at individual level with age group but without vaccine types.

```{r}

source(paste0(path_data_code,"/vaccination.R"))
            
```


# Descriptive
## daily

### vaccination progress regardless of vac_type and dose

```{r}

# # pop weighing
# vacc_BUND %>% group_by(rep_date) %>%
#   summarise_if(is.numeric, sum)%>%
#   mutate(vac_mean7da = zoo::rollmean(vac_n, k = 7, fill = NA))%>%
#   ggplot(aes(x = rep_date))+
#   geom_line(aes(y=vac_n/NRW_pop*100000, color = "vac_n/NRW_pop*100000"), size =1)+
#   geom_line(aes(y=vac_mean7da/NRW_pop*100000,color = "vac_mean7da/NRW_pop*100000"), size = 1)+
#   # facet_grid(row = vars(dose))+
#   labs(x = "Vaccination time", y = "Vacinated dose per 100k pop", color ="") +
#   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
#   ggtitle(" Vaccination against SAR-CoV-2 in NRW " )+
#   scale_color_manual(values=c("vac_n/NRW_pop*100000"="blue","vac_mean7da/NRW_pop*100000"="red"),
#                      labels = c("Raw number",
#                                 "Rolling ave.7days"))+
#   theme_classic()+
#   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
#         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
#         axis.title = element_text(colour = "black", size = 15, face = "bold"),
#         legend.background = element_blank(),
#         legend.key = element_blank(),
#         legend.position = c(0.2,0.8),
#         legend.text = element_text(colour = "black", size = 15),
#         legend.title = element_text(colour = "black", size = 16, face = "bold"),
#         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
#         strip.text = element_text(colour = "black", size = 10, face = "bold"))
# 

# No pop weighing

vacc_BUND %>% group_by(rep_date) %>%
  summarise_if(is.numeric, sum)%>%
  mutate(vac_mean7da = zoo::rollmean(vac_n, k = 7, fill = NA))%>%
  ggplot(aes(x = rep_date))+
  geom_line(aes(y=vac_n/1000, color = "vac_n"), size =1)+
  geom_line(aes(y=vac_mean7da/1000,color = "vac_mean7da"), size = 1)+
  # facet_grid(row = vars(dose))+
  labs(x = "Vaccination time", y = "Vacinated dose (thousand)", color ="") +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  ggtitle(" Vaccination against SAR-CoV-2 in NRW " )+
  scale_color_manual(values=c("vac_n"="blue","vac_mean7da"="red"),
                     labels = c("Raw number",
                                "Rolling ave.7days"))+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = c(0.2,0.8),
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))



```

### vaccination vs dose

```{r}

#vaccination_by date#############################
##No pop weighing
p1 <- vacc_BUND%>% group_by(rep_date,dose)%>%
              summarise_if(is.numeric,sum)%>%
  ggplot(aes(x = rep_date, y=vac_n/1000, group = dose))+
  # geom_bar(position="fill", stat="identity")+
  geom_line(aes(color=dose))+
  # facet_grid(row = vars(dose))+
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  labs(x = "Vaccination time", y = "Vacinated dose (thousand)") +
  ylim(0,500)+
  ggtitle("Vaccination against SAR-CoV-2 in NRW")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = c(0.12,0.8),
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

p1

# ##pop weighing
# p1 <- vacc_BUND%>% group_by(rep_date,dose)%>%
#               summarise_if(is.numeric,sum)%>%
#   ggplot(aes(x = rep_date, y=vac_n/NRW_pop*100000, group = dose))+
#   # geom_bar(position="fill", stat="identity")+
#   geom_line(aes(color=dose))+
#   # facet_grid(row = vars(dose))+
#   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
#   labs(x = "Vaccination time", y = "Vacinated individual/100k") +
#   ylim(0,1200)+
#   ggtitle("Vaccination against SAR-CoV-2 in NRW")+
#   theme_classic()+
#   theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
#         axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
#         axis.title = element_text(colour = "black", size = 15, face = "bold"),
#         legend.background = element_blank(),
#         legend.key = element_blank(),
#         legend.position = c(0.12,0.8),
#         legend.text = element_text(colour = "black", size = 15),
#         legend.title = element_text(colour = "black", size = 16, face = "bold"),
#         plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
#         strip.text = element_text(colour = "black", size = 10, face = "bold"))
# 
# p1

# p2 <- vacc_LK %>% group_by(rep_date,dose)%>%
#               summarise_if(is.numeric,sum)%>%
#   ggplot(aes(x = rep_date, y=vac_n/NRW_pop*100000, group = dose))+
#   # geom_bar(position="fill", stat="identity")+
#   geom_line(aes(color=dose))+
#   # facet_grid(row = vars(dose))+
#   labs(x = "Vaccination time", y = "Vacinated individual/1ook") +
#     ylim(0,1200)+
#   ggtitle("NRW_vaccination_daily [LK dataset]")+
#   theme(axis.text.x = element_text(angle = 90),
#         plot.title = element_text(face = "bold",hjust = 0.5))+
#   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))
# 
# 
# # multiple plots in the same page 
# ggarrange(p1+rremove("x.text"), p2, 
#           labels = c("A", "B"),
#           ncol = 1, nrow = 2)

```

### Vaccination vs vaccine type

#### Absolute number

```{r results='asis'}

# reshape data
vac_type <- vacc_BUND %>% dplyr::select(rep_date,vac_type,vac_n)%>%
  group_by(rep_date,vac_type)%>%
  summarise_if(is.numeric,sum)# count at date level

vac_type <- vac_type %>%
  pivot_wider(names_from = vac_type, values_from = vac_n)#Transposing row values to column
vac_type [is.na(vac_type)] <- 0 # replace NAs value with 0
vac_type <- as.data.frame(vac_type)

#rolling average for smoother
vac_type <- vac_type %>%
mutate(Comirnaty_7da = zoo::rollmean(Comirnaty, k =7, fill = NA),
         Janssen_7da= zoo::rollmean(Janssen, k =7, fill = NA),
         Moderna_7da= zoo::rollmean(Moderna, k =7, fill = NA),
         AstraZeneca_7da= zoo::rollmean(AstraZeneca, k =7, fill = NA)
         )

vac_type <- vac_type%>% dplyr::select(-c("Comirnaty","Janssen","Moderna","AstraZeneca"))
colnames(vac_type) <- c("rep_date","Comirnaty","Janssen","Moderna","AstraZeneca")

vac_type <- na.omit(vac_type) # remove rows with NA due to rolling ave. step


vac_type <- reshape2::melt(vac_type, id.vars = c("rep_date"))


# stacked area chart
p <- ggplot(vac_type, aes(x=rep_date, y=value/1000, fill=variable)) + 
  geom_area()+
  scale_fill_manual(values=c("#d7191c", "#fdae61", "#abdda4", "#2b83ba"), name="Vaccine Type")+
  # scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days", 
  #              limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
  #              expand = c(0, 0)) +
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  labs(x = " ", y = "Vaccinated dose (thousand)_ave.7days") +
  ggtitle("COVID-19 Vaccination in NRW")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = c(0.12,0.8),
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

# grid.arrange(p,nrow = 1)
print(p)

```

#### Proportion

Check why the white appears in such a pattern!

```{r}
# Compute percentages with dplyr
# by vaccine type
p <- vac_type  %>%
  group_by(rep_date, variable) %>%
 ggplot(aes(x=rep_date, y=value, fill=variable)) + 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values=c("#d7191c", "#fdae61", "#abdda4", "#2b83ba"), name="Vaccine Type")+
   # scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days",
   #             limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
   #             expand = c(0, 0)) +
   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  labs(x = " ", y = "") +
    ggtitle("COVID-19 Vaccination in NRW")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        # legend.position = c(0.12,0.8),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

print(p)

# by age
vac_age <- vacc %>%group_by(rep_week_date,age_vac)%>%
  summarise(vac_n= sum(vac_n))

vac_age_plot <- vac_age  %>%
  group_by(rep_week_date, vac_n) %>%
 ggplot(aes(x=rep_week_date, y=vac_n, fill=age_vac)) + 
  geom_bar(position="fill", stat="identity")+
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values=c("#d7191c", "#fdae61", "#abdda4", "#2b83ba"), name="Age of vaccination")+
   # scale_x_date(date_labels="%Y-%m-%d", date_breaks = "14 days",
   #             limits = c(as.Date("2020-03-01"),as.Date("2021-12-30")),
   #             expand = c(0, 0)) +
   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  labs(x = " ", y = "") +
    ggtitle("")+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        # legend.position = c(0.12,0.8),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))


print(vac_age_plot)

```


### cum vac over time

```{r}
#cum vac over time ###################

vac_alltype1 <- vacc_BUND %>%filter(dose==1)%>% group_by(rep_date) %>%
  summarise_if(is.numeric, sum)
vac_alltype1 <- vac_alltype1 %>% dplyr::select(-c("vac_week"))# delete vac_week as it's wrong due to previous step
vac_alltype1$vac_n_cum <- cumsum(vac_alltype1$vac_n)
vac_alltype1$dose <- 1

vac_alltype2 <- vacc_BUND %>%filter(dose==2)%>% group_by(rep_date) %>%
  summarise_if(is.numeric, sum)
vac_alltype2 <- vac_alltype2 %>% dplyr::select(-c("vac_week"))# delete vac_week as it's wrong due to previous step
vac_alltype2$vac_n_cum <- cumsum(vac_alltype2$vac_n)
vac_alltype2$dose <- 2

vac_alltype3 <- vacc_BUND %>%filter(dose=="booster")%>% group_by(rep_date) %>%
  summarise_if(is.numeric, sum)
vac_alltype3 <- vac_alltype3%>% dplyr::select(-c("vac_week"))# delete vac_week as it's wrong due to previous step
vac_alltype3$vac_n_cum <- cumsum(vac_alltype3$vac_n)
vac_alltype3$dose <- "booster"

vac_alltype <- rbind(vac_alltype1,vac_alltype2,vac_alltype3)


vac_cum_plot <- ggplot(vac_alltype,
       aes(x = rep_date,y=vac_n_cum/NRW_pop*100, color = dose))+
  # geom_bar(position="fill", stat="identity")+
  geom_line()+
  #wave3
  geom_vline(xintercept = as.Date("2021-02-17"))+
  geom_text(aes(x =as.Date("2021-02-17"),label = "Wave 3",y=88),color="red",angle=90, vjust = 1.2,text=element_text(size=11))+
  #Wave4
   geom_vline(xintercept = as.Date("2021-07-28"))+
  geom_text(aes(x =as.Date("2021-07-28"),label = "Wave 4",y=88),color="red",angle=90, vjust = 1.2,text=element_text(size=11))+
  # facet_grid(row = vars(dose))+
  ylim(0,100)+
  labs(x = "Reported week commencing", y = "Acc. % of vaccinated poulation") +
  ggtitle("")+
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days",
               limits = c(as.Date("2021-01-05"),as.Date("2021-12-31")),
               expand = c(0, 0))+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        # legend.position = c(0.12,0.8),
        legend.position = "right",
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),

        
                strip.text = element_text(colour = "black", size = 10, face = "bold"))

vac_cum_plot

# Multiple pülot in one page
panel <- ggarrange(vac_age_plot + rremove("x.text") , 
          vac_cum_plot ,
         # labels = c("A", "B"),
         align = "v",
         heights = c(0.35, 0.65),
         ncol = 1, nrow = 2)

annotate_figure(panel, 
                left = textGrob("", rot = 90, vjust = 0.5, gp = gpar(cex = 1.5)))
            





```


## weekly

```{r}
# vaccination by week#############################

# vac_byweek <- vacc_LK %>% group_by(vac_week_date, dose) %>%
#   summarise_if(is.numeric,sum) # sum the numeric cols by group above, keep the names

#[BUND dataset]
p1 <- vacc_BUND %>% group_by(vac_week_date, dose) %>%
  summarise_if(is.numeric,sum)%>%
  ggplot(aes(x = vac_week_date, y=vac_n/1000, group = dose))+
  # geom_bar(position="fill", stat="identity")+
  geom_line(aes(color=dose))+
  # facet_grid(row = vars(dose))+
  labs(x = "Vaccination time", y = "Vacinated dose (thousand)") +
  ggtitle("Vaccination against SAR-CoV-2 in NRW _weekly report")+
  scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))+
  theme_classic()+
  theme(axis.text.x = element_text(colour = "black", size = 10, angle = 90, hjust = 0.5, vjust = 0,5),
        axis.text.y = element_text(colour = "black", size = 15, face = "bold"),
        axis.title = element_text(colour = "black", size = 15, face = "bold"),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.position = c(0.12,0.8),
        legend.text = element_text(colour = "black", size = 15),
        legend.title = element_text(colour = "black", size = 16, face = "bold"),
        plot.title = element_text(colour = "black", size = 14, face = "bold",hjust = 0.5),
        strip.text = element_text(colour = "black", size = 10, face = "bold"))

p1

##[LK dataset]
# p2 <- vacc_LK %>% group_by(vac_week_date, dose) %>%
#   summarise_if(is.numeric,sum)%>%
#   ggplot(aes(x = vac_week_date, y=vac_n/NRW_pop*100000, group = dose))+
#   # geom_bar(position="fill", stat="identity")+
#   geom_line(aes(color=dose))+
#   # facet_grid(row = vars(dose))+
#   labs(x = "Vaccination time", y = "Vacinated individual per 100k") +
#   ggtitle("NRW_vaccination_weekly [LK dataset]")+
#   theme(axis.text.x = element_text(angle = 90),
#         plot.title = element_text(face = "bold",hjust = 0.5))+
#   scale_x_date(date_labels="%Y-%m-%d", date_breaks = "7 days", expand = c(0, 0))
# 
# 
# # multiple plots in the same page 
# ggarrange(p1+rremove("x.text"), p2, 
#           labels = c("A", "B"),
#           ncol = 1, nrow = 2)

```

